---
title: "Analysis of Global and Country Max & Global Variables"
author: "Nathalie Guibert"
date: "`r Sys.Date()`"
output: pdf_document
---

# Analysis file


## Setup is being executed.

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, tidy.opts = list(width.cutoff = 30), tidy = TRUE)
knitr::opts_chunk$set(fig.width=6, fig.height=4)

# Load necessary libraries
library("lfe")
library("ggplot2")
library("ggExtra")
library("countrycode")
library("readr")
library("dplyr")
library("fixest")
library("texreg")
library("texreg")
library("formatR")
library("stargazer")

# Set working directory
setwd("C:/Users/whatt/Desktop/2024_ResAss_UZHIPZ_WeidmannDonnay/work24DonnayWeidmann/data")

# Load the data
joined_data <- read_csv("joined_data.csv")

# Add country name and region for future fixed effects
joined_data$country_name <- countrycode(joined_data$gwid.x, "gwn", "country.name")
joined_data$region <- countrycode(joined_data$gwid.x, "gwn", "region")

```

## Version 1: Current Version


### Plots

#### Global / Country Max plots; Goal: Compare Global and Country Orientation of Posts

##### Compare global_max scores and country_max scores based on posts  

Here we would like to see if organisations tend to communicate more on a global or national 
level by comparing their global_max and country_max scores (both metrics measure 
the likelihood of content being about global or national topics).
Here we compare global_max scores and country_max scores using a regression line to detect
a correlation; as one of those two dimensions for a post should be higher as the 
other one, as we would expect that an organisation communicates either rather on 
a global or on a country level.

```{r, include=FALSE}
plt_global_country_max <- ggplot(joined_data, aes(x = global_max, y = country_max)) +
  geom_point(alpha = 0.6) +  # Add transparency to avoid overplotting
  geom_smooth(method = "lm", col = "blue", se = FALSE) +  # Add a linear regression line
  labs(title = "Global Max vs Country Max",
       x = "Global Max",
       y = "Country Max") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -2),
    axis.title.y = element_text(vjust = 2)
  ) 

ggExtra::ggMarginal(plt_global_country_max, size = 2,type = "histogram", xparams= list(fill="lightblue"), yparams =list(fill="lightgreen"))

ggsave("global_country_max_scatter.jpg", plot= plt_global_country_max, bg = "white")
 
  
```

Same but posts divided in regions.

```{r, include=FALSE}
plt_global_country_max_regions <- ggplot(joined_data, aes(x = global_max, y = country_max, colour=region)) +
  geom_point(alpha = 0.5) +  
  geom_smooth(method = "lm", col = "black", se = FALSE) +  
  labs(title = "Scatterplot: Global Max vs Country Max",
       x = "Global Max",
       y = "Country Max") +
  theme_minimal() 

ggExtra::ggMarginal(plt_global_country_max_regions, groupColour = TRUE, groupFill = TRUE)

ggsave("global_country_max_regions.jpg", plot= plt_global_country_max_regions, bg = "white")
```

Contrary to our assumption, the plot indicates a positive correlation between
country_max and global_max scores, thus, implying that if the global max score is 
higher then also the country max score is higher. Thus, this may mean that posts 
that generally have a relation to a geographical level will spur up scores on both
country and global level. Disclaimer: These preliminary results should be used 
with caution: Currently there is a data issue which maps these scores to the wrong
posts in another dataset. Furthermore, it should also be mentioned that there 
are many posts with a zero score on a country level, whereas zero scores barely
exist for the global scores.

##### Country  


Global Max by Country  

Here we assess how the likelihood of global conversations varies across different countries.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
plt_globalmax_cntry <- ggplot(joined_data, aes(x = as.factor(country_name), y = global_max)) +
  geom_boxplot(fill = "lightblue", color = "black") +  # Set a single fill color and outline color
  labs(title = "Global Max by Country",
       x = "Country",
       y = "Global Max") +  
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45), 
        axis.title.y = element_text(vjust = 0.5),
        legend.position = "none") 

ggsave("Global_Max_Country.jpg", plot = plt_globalmax_cntry, bg="white")
plt_globalmax_cntry
```  

Interpretation: The probability of having global conversations varies widely 
between countries but for most countries the probability is relatively low.


Country Max by Country  

Here we assess how the likelihood of national conversations varies across different countries.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
plt_cntrymax_cntry <- ggplot(joined_data, aes(x = as.factor(country_name), y = country_max)) +
  geom_boxplot(fill = "lightgreen", color="black") +
  labs(title = "Country Max by Country",
       x = "Country",
       y = "Country Max") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45), 
        axis.title.y = element_text(vjust = 0.5),
        legend.position = "none") 
ggsave("Country_Max_Country.jpg", plot = plt_cntrymax_cntry, bg="white")
plt_cntrymax_cntry
```

Interpretation: The probability of having national conversations stays for the bigger part in most countries 
below a half.


##### Channel Type  

Here, we check whether the type of channel has an impact of the globality and
nationality of the posts.

Global Max by Channel Type

```{r, echo=FALSE, warning=FALSE, message=FALSE}
plt_globalmax_channel_type <- ggplot(joined_data, aes(x = as.factor(channel_type), y = global_max)) +
  geom_boxplot() +
  labs(title = "Global Max by Channel Type",
       x = "Channel Type",
       y = "Global Max") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Global_Max_Channel_Type.jpg", plot = plt_globalmax_channel_type, bg="white")
plt_globalmax_channel_type
```  

Interpretation: This plot is currently not really pertinent, as only one platform has been registered in the 
data.


Country Max by Channel Type 

```{r, echo=FALSE, warning=FALSE, message=FALSE}
plt_cntrymax_channel_type <- ggplot(joined_data, aes(x = as.factor(channel_type), y = country_max)) +
  geom_boxplot() +
  labs(title = "Country Max by Channel Type",
       x = "Channel Type",
       y = "Country Max") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Country_Max_Channel_Type.jpg", plot = plt_cntrymax_channel_type, bg="white")
plt_cntrymax_channel_type
```

Interpretation: This plot is currently not really pertinent, as only one platform has been registered in the 
data.

##### Multiethnic flag  

Here, we examine whether an organisation's status as multiethnic influences the
global or national focus of its posts.  

Global Max by Multiethnicity flag

```{r, echo=FALSE, warning=FALSE, message=FALSE}
plt_globalmax_multiethnicity <- ggplot(joined_data, aes(x = as.factor(multiethnic_flag), y = global_max)) +
  geom_boxplot() +
  labs(title = "Global Max by Multiethnicity",
       x = "Multiethnicity",
       y = "Global Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Global_Max_Multiethnicity.jpg", plot = plt_globalmax_multiethnicity, bg="white")
plt_globalmax_multiethnicity
```  

Interpretation: If the organisation is multiethnic, the conversations are basically all global, whereas when the
organisation isn't multiethnic, the conversation has a tendency to not be global but with many outliers.

Country Max by Multiethnicity flag

```{r, echo=FALSE, warning=FALSE, message=FALSE}
plt_cntrymax_multiethnicity <- ggplot(joined_data, aes(x = as.factor(multiethnic_flag), y = country_max)) +
  geom_boxplot() +
  labs(title = "Country Max by Multiethnicity",
       x = "Multiethnicity",
       y = "Country Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() + 
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Country_Max_Multiethnicity.jpg", plot = plt_cntrymax_multiethnicity, bg="white")
plt_cntrymax_multiethnicity
```  

Interpretation: Independent of the multiethnicity of organisations, the conversations have a lower probability 
to be about national topics, albeit when the organisation is not multiethnic there are also many outliers that 
the conversation is indeed rather focussed on national issues.

##### Organisation Age  

Here, we examine whether an organisation's age has an impact on the global or national 
focus of its posts.  
```{r, eval=FALSE, include=FALSE}
#Disclaimer: I am not happy with how these plots look like yet.
#Idea: Perhaps box plots for global and then group the organisation age by 10 years.
```

Global Max by Organisation age

```{r, echo=FALSE, warning=FALSE, message=FALSE}
plt_globalmax_org_age <- ggplot(joined_data, aes(x = org_age, y = global_max)) +
  geom_jitter() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Global Max by Organization Age",
       x = "Organization Age",
       y = "Global Max") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Global_Max_Org_Age.jpg", plot = plt_globalmax_org_age, bg="white")
plt_globalmax_org_age
```  

Interpretation: In the plot is a slight tendency that with growing age posts become more likely to be global, 
however, the data points are too randomly distributed to make a general assumption.


Country Max by Organisation age

```{r, echo=FALSE, warning=FALSE, message=FALSE}
plt_cntrymax_org_age <- ggplot(joined_data, aes(x = org_age, y = country_max)) +
  geom_jitter() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Country Max by Organization Age",
       x = "Organization Age",
       y = "Country Max") +
  theme_minimal() + 
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Country_Max_Org_Age.jpg", plot = plt_cntrymax_org_age, bg="white")
plt_cntrymax_org_age
```  

Interpretation: Same as above, only the tendency to be more nation-minded is slightly higher.


##### Static exclusion status   

In these plots, we check whether an exclusionary status of the organisation has
an impact on the globality and nationality of a organisation's posts.  

Global Max by Static exclusion status

```{r, echo=FALSE, warning=FALSE, message=FALSE}
plt_globalmax_static_excl <- ggplot(na.omit(joined_data[, c("global_max", "status_excl_epr_static")]), aes(x = as.factor(status_excl_epr_static), y = global_max)) +
  geom_boxplot() +
  labs(title = "Global Max by Static Exclusion Status",
       x = "Static Exclusion Status",
       y = "Global Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Global_Max_static_exclusion.jpg", plot = plt_globalmax_static_excl, bg="white")
plt_globalmax_static_excl
```

Interpretation: The probability of having global posts is for both excluded and included organisations 
relatively low, albeit there are many outliers in both cases.

Country Max by Static exclusion status  

```{r, echo=FALSE, warning=FALSE, message=FALSE}
plt_cntrymax_static_excl <- ggplot(na.omit(joined_data[, c("country_max", "status_excl_epr_static")]), aes(x = as.factor(status_excl_epr_static), y = country_max)) +
  geom_boxplot() +
  labs(title = "Country Max by Static Exclusion Status",
       x = "Static Exclusion Status",
       y = "Country Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -2),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Country_Max_static_exclusion.jpg", plot = plt_cntrymax_static_excl, bg="white")
plt_cntrymax_static_excl
```

Interpretation: Same result as above is applicable to the probability of having posts focussed on country 
issues. Thus, I would argue that the status of an organisation does neither explain the likelihood of globality 
of posts nor the likelihood of a nation-focus of posts.

Disclaimer: Plots for global variable, as well as exclusion status per year are a work in process.  


### new data

Global Max by primary channel
```{r}
plt_globmax_prim_chan <- ggplot(na.omit(joined_data[, c("global_max", "primary")]), aes(x = as.factor(primary), y = global_max)) +
  geom_boxplot() +
  labs(title = "Global Max by Primary Channel",
       x = "Primary Channel",
       y = "Global Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Global_Max_primary.jpg", plot = plt_globmax_prim_chan, bg="white")
plt_globmax_prim_chan
```

Country Max by primary channel
```{r}
plt_cntrymax_prim_chan <- ggplot(na.omit(joined_data[, c("country_max", "primary")]), aes(x = as.factor(primary), y = country_max)) +
  geom_boxplot() +
  labs(title = "Country Max by Primary Channel",
       x = "Primary Channel",
       y = "Country Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Country_Max_primary.jpg", plot = plt_cntrymax_prim_chan, bg="white")
plt_cntrymax_prim_chan
```


Global Max by election participation
```{r}
plt_globmax_elect_part <- ggplot(na.omit(joined_data[, c("global_max", "elect_part")]), aes(x = as.factor(elect_part), y = global_max)) +
  geom_boxplot() +
  labs(title = "Global Max by Electoral Participation",
       x = "Electoral Participation",
       y = "Global Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Global_Max_elect_part.jpg", plot = plt_globmax_elect_part, bg="white")
plt_globmax_elect_part
```


Country Max by election participation
```{r}
plt_cntrymax_elect_part <- ggplot(na.omit(joined_data[, c("country_max", "elect_part")]), aes(x = as.factor(elect_part), y = country_max)) +
  geom_boxplot() +
  labs(title = "Country Max by Electoral Participation",
       x = "Electoral Participation",
       y = "Country Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Country_Max_elect_part.jpg", plot = plt_cntrymax_elect_part, bg="white")
plt_cntrymax_elect_part
```



Global Max by language prediction
```{r}
plt_globmax_lang_pred <- ggplot(joined_data, aes(x = as.factor(language_pred), y = global_max)) +
  geom_boxplot(fill = "lightgreen", color="black") +
  labs(title = "Global Max by Language Prediction",
       x = "Language Prediction",
       y = "Global Max") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45), 
        axis.title.y = element_text(vjust = 0.5),
        legend.position = "none") 

ggsave("Global_Max_lang_pred.jpg", plot = plt_globmax_lang_pred, bg="white", width = 20, height = 8, units = "cm")

plt_globmax_cntry
```

Country Max by language prediction
```{r}
plt_cntrymax_lang_pred <- ggplot(joined_data, aes(x = as.factor(language_pred), y = country_max)) +
  geom_boxplot(fill = "lightgreen", color="black") +
  labs(title = "Country Max by Language Prediction",
       x = "Language Prediction",
       y = "Country Max") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45), 
        axis.title.y = element_text(vjust = 0.5),
        legend.position = "none") 

ggsave("Cntry_Max_lang_pred.jpg", plot = plt_cntrymax_lang_pred, bg="white", width = 20, height = 8, units = "cm")

plt_cntrymax_lang_pred
```


Global Max by education language 
```{r}
plt_globmax_educ_lang <- ggplot(na.omit(joined_data[, c("global_max", "ed_language1")]), aes(x = as.factor(ed_language1), y = global_max)) +
  geom_boxplot(fill = "lightgreen", color="black") +
  labs(title = "Global Max by Education Language",
       x = "Education Language",
       y = "Global Max") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45), 
        axis.title.y = element_text(vjust = 0.5),
        legend.position = "none") 

ggsave("Global_Max_educ_lang.jpg", plot = plt_globmax_educ_lang, bg="white", width = 20, height = 8, units = "cm")

plt_globmax_educ_lang
```

Country Max by education language 
```{r}
plt_cntrymax_educ_lang <- ggplot(na.omit(joined_data[, c("country_max", "ed_language1")]), aes(x = as.factor(ed_language1), y = country_max)) +
  geom_boxplot(fill = "lightgreen", color="black") +
  labs(title = "Country Max by Education Language",
       x = "Education Language",
       y = "Country Max") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45), 
        axis.title.y = element_text(vjust = 0.5),
        legend.position = "none") 

ggsave("Cntry_Max_educ_lang.jpg", plot = plt_cntrymax_educ_lang, bg="white", width = 20, height = 8, units = "cm")

plt_cntrymax_educ_lang
```


Global Max by statusname
```{r}
plt_globmax_statusname <- ggplot(na.omit(joined_data[, c("global_max", "statusname")]), aes(x = as.factor(statusname), y = global_max)) +
  geom_boxplot(fill = "lightgreen", color="black") +
  labs(title = "Global Max by Statusname",
       x = "Statusname",
       y = "Global Max") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45), 
        axis.title.y = element_text(vjust = 0.5),
        legend.position = "none") 

ggsave("Global_Max_statusname.jpg", plot = plt_globmax_statusname, bg="white")

plt_globmax_statusname
```

Country Max by statusname
```{r}
plt_cntrymax_statusname <- ggplot(na.omit(joined_data[, c("country_max", "statusname")]), aes(x = as.factor(statusname), y = country_max)) +
  geom_boxplot(fill = "lightgreen", color="black") +
  labs(title = "Country Max by Statusname",
       x = "Statusname",
       y = "Country Max") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45), 
        axis.title.y = element_text(vjust = 0.5),
        legend.position = "none") 

ggsave("Cntry_Max_statusname.jpg", plot = plt_cntrymax_statusname, bg="white")

plt_cntrymax_statusname
```


Global Max by government power
```{r}
plt_globmax_gov_pow <- ggplot(na.omit(joined_data[, c("global_max", "gov_pow")]), aes(x = as.factor(gov_pow), y = global_max)) +
  geom_boxplot() +
  labs(title = "Global Max by Government Power",
       x = "Government Power",
       y = "Global Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Global_Max_gov_pow.jpg", plot = plt_globmax_gov_pow, bg="white")
plt_globmax_gov_pow
```

Country Max by government power
```{r}
plt_cntrymax_gov_pow <- ggplot(na.omit(joined_data[, c("country_max", "gov_pow")]), aes(x = as.factor(gov_pow), y = country_max)) +
  geom_boxplot() +
  labs(title = "Country Max by Government Power",
       x = "Government Power",
       y = "Country Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Cntry_Max_gov_pow.jpg", plot = plt_cntrymax_gov_pow, bg="white")
plt_cntrymax_gov_pow
```


Global Max by regional autonomy
```{r}
plt_globmax_reg_aut <- ggplot(na.omit(joined_data[, c("global_max", "reg_autonom")]), aes(x = as.factor(reg_autonom), y = global_max)) +
  geom_boxplot() +
  labs(title = "Global Max by Regional Autonomy",
       x = "Regional Autonomy",
       y = "Global Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Global_Max_reg_aut.jpg", plot = plt_globmax_reg_aut, bg="white")
plt_globmax_reg_aut
```

Country Max by regional autonomy
```{r}
plt_cntrymax_reg_aut <- ggplot(na.omit(joined_data[, c("country_max", "reg_autonom")]), aes(x = as.factor(reg_autonom), y = country_max)) +
  geom_boxplot() +
  labs(title = "Country Max by Regional Autonomy",
       x = "Regional Autonomy",
       y = "Country Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Cntry_Max_reg_aut.jpg", plot = plt_cntrymax_reg_aut, bg="white")
plt_cntrymax_reg_aut
```



Global Max by separatism / irridentism
```{r}
plt_globmax_sep_irred <- ggplot(na.omit(joined_data[, c("global_max", "sep_irred")]), aes(x = as.factor(sep_irred), y = global_max)) +
  geom_boxplot() +
  labs(title = "Global Max by Separatism/Irridentism",
       x = "Separatism/Irridentism",
       y = "Global Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Global_Max_sep_irred.jpg", plot = plt_globmax_sep_irred, bg="white")
plt_globmax_sep_irred
```

Country Max by separatism / irridentism
```{r}
plt_cntrymax_sep_irred <- ggplot(na.omit(joined_data[, c("country_max", "sep_irred")]), aes(x = as.factor(sep_irred), y = country_max)) +
  geom_boxplot() +
  labs(title = "Country Max by Separatism/Irridentism",
       x = "Separatism/Irridentism",
       y = "Country Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Cntry_Max_sep_irred.jpg", plot = plt_cntrymax_sep_irred, bg="white")
plt_cntrymax_sep_irred
```


Global Max by ethnic claim
```{r}
plt_globmax_eth_claim <- ggplot(na.omit(joined_data[, c("global_max", "eth_claim")]), aes(x = as.factor(eth_claim), y = global_max)) +
  geom_boxplot() +
  labs(title = "Global Max by Ethnic Claim",
       x = "Ethnic Claim",
       y = "Global Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Global_Max_eth_claim.jpg", plot = plt_globmax_eth_claim, bg="white")
plt_globmax_eth_claim
```

Country Max by ethnic claim
```{r}
plt_cntrymax_eth_claim <- ggplot(na.omit(joined_data[, c("country_max", "eth_claim")]), aes(x = as.factor(eth_claim), y = country_max)) +
  geom_boxplot() +
  labs(title = "Country Max by Ethnic Claim",
       x = "Ethnic Claim",
       y = "Country Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Cntry_Max_eth_claim.jpg", plot = plt_cntrymax_eth_claim, bg="white")
plt_cntrymax_eth_claim
```



#### Prop Global


Distribution of global post proportions over all organisations
```{r}
unique_organisations <- joined_data %>%
  distinct(org_id_from_coll, .keep_all = TRUE)

prop_of_glob_props <- ggplot(unique_organisations, aes(x = prop_global)) +
  geom_histogram(binwidth = 0.05, fill = "skyblue", color = "black") +
  labs(
    title = "Distribution of Global Post Proportions",
    x = "Proportion of global posts",
    y = "Number of Organisations"
  ) +
  theme_minimal()

ggsave("Proportions_GlobalProportions.jpg", plot = prop_of_glob_props, bg="white")
prop_of_glob_props

```




Per country
```{r}
plt_propglob_cntry <- ggplot(joined_data, aes(x = as.factor(country_name), y = prop_global)) +
  geom_boxplot(fill = "beige", color="black") +
  labs(title = "Proportion of global posts by Country",
       x = "Country",
       y = "Global Proportion") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90), 
        axis.title.y = element_text(vjust = 0.5),
        legend.position = "none") 
#ggsave("Prop_Glob_Country.jpg", plot = plt_propglob_cntry, bg="white")
plt_propglob_cntry
```


Per Region 

```{r}
plt_propglob_region <- ggplot(joined_data, aes(x = as.factor(region), y = prop_global)) +
  geom_boxplot(fill = "beige", color="black") +
  labs(title = "Proportion of global posts by Region",
       x = "Region",
       y = "Global Proportion") +
  theme_minimal() +
  theme(axis.title.y = element_text(vjust = 0.5),
        legend.position = "none") 
#ggsave("Prop_Global_Region.jpg", plot = plt_propglob_region, bg="white")
plt_propglob_region
```
 
#### Channel Type

```{r, echo=FALSE, warning=FALSE, message=FALSE}
plt_prop_glob_channel_type <- ggplot(joined_data, aes(x = as.factor(channel_type), y = prop_global)) +
  geom_boxplot() +
  labs(title = "Global proportion of all posts by Channel Type",
       x = "Channel Type",
       y = "Proportion of global posts") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
#ggsave("Prop_Global_Channel_Type.jpg", plot = plt_prop_glob_channel_type, bg="white")
plt_prop_glob_channel_type
```  


by Multiethnicity

```{r}
plt_prop_glob_multiethnicity <- ggplot(joined_data, aes(x = as.factor(multiethnic_flag), y = prop_global)) +
  geom_boxplot() +
  labs(title = "Global proportion of all posts by Multiethnicity",
       x = "Multiethnicity",
       y = "Proportion of global posts") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
#ggsave("Prop_glob_Multiethnicity.jpg", plot = plt_prop_glob_multiethnicity, bg="white")
plt_prop_glob_multiethnicity
```


Organisation Age
```{r}
plt_prop_glob_org_age <- ggplot(joined_data, aes(x = org_age, y = prop_global)) +
  geom_jitter() +
  geom_smooth(method = "lm", se = TRUE) +
  labs(title = "Global proportion of all posts by Organization Age",
       x = "Organization Age",
       y = "Proportion of global posts") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
#ggsave("Prop_Global_Org_Age.jpg", plot = plt_prop_glob_org_age, bg="white")
plt_prop_glob_org_age
```




Static Exclusion Status 

```{r}
plt_prop_glob_static_excl <- ggplot(na.omit(joined_data[, c("prop_global", "status_excl_epr_static")]), aes(x = as.factor(status_excl_epr_static), y = prop_global)) +
  geom_boxplot() +
  labs(title = "Global proportion of all posts by Static Exclusion Status",
       x = "Static Exclusion Status",
       y = "Proportion of global posts") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
#ggsave("Prop_glob_static_exclusion.jpg", plot = plt_prop_glob_static_excl, bg="white")
plt_prop_glob_static_excl
```


Primary Account
```{r}
plt_prop_glob_primary <- ggplot(joined_data, aes(x = as.factor(primary), y = prop_global)) +
  geom_boxplot() +
  labs(title = "Global proportion of all posts by Primary Account",
       x = "Primary Account",
       y = "Proportion of global posts") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
#ggsave("Prop_Global_Primary.jpg", plot = plt_prop_glob_primary, bg="white")
plt_prop_glob_primary
```

Election Participation
```{r}
plt_prop_glob_elect_part <- ggplot(joined_data, aes(x = as.factor(elect_part), y = prop_global)) +
  geom_boxplot() +
  labs(title = "Global proportion of all posts by Electoral Participation of organisation",
       x = "Electoral Participation",
       y = "Proportion of global posts") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
#ggsave("Prop_Global_Elect_Part.jpg", plot = plt_prop_glob_elect_part, bg="white")
plt_prop_glob_elect_part
```

Language Prediction
```{r, fig.width=10, fig.height=8}
plt_propglob_langpred <- ggplot(joined_data, aes(x = as.factor(language_pred), y = prop_global)) +
  geom_boxplot(fill = "beige", color = "black", position=position_dodge(width=3)) +
  labs(
    title = "Proportion of Global Posts by Language",
    x = "Language",
    y = "Global Proportion"
  ) +
  theme_minimal() +
  theme(axis.title.y = element_text(vjust = 0.5)) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))  # Staggers labels


#ggsave("Prop_Global_Lang.jpg", plot = plt_propglob_langpred, bg="white")
plt_propglob_langpred
```

Language in Education
```{r, fig.width=10, fig.height=8}
plt_propglob_langeduc <- ggplot(joined_data, aes(x = as.factor(ed_language1), y = prop_global)) +
  geom_boxplot(fill = "beige", color = "black", position=position_dodge(width=3)) +
  labs(
    title = "Proportion of Global Posts by Language in Education",
    x = "Language in education",
    y = "Global Proportion"
  ) +
  theme_minimal() +
  theme(axis.title.y = element_text(vjust = 0.5)) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))  # Staggers labels


#ggsave("Prop_Global_Lang_Educ.jpg", plot = plt_propglob_langeduc, bg="white")
plt_propglob_langeduc
```


Statusname:
```{r}
plt_prop_glob_statusname <- ggplot(joined_data, aes(x = as.factor(statusname), y = prop_global)) +
  geom_boxplot() +
  labs(title = "Global proportion of all posts by status",
       x = "Status",
       y = "Proportion of global posts") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2),
    axis.text.x = element_text(angle = 90)
  ) 
#ggsave("Prop_Global_Status.jpg", plot = plt_prop_glob_statusname, bg="white")
plt_prop_glob_statusname
```

Government power
```{r}
plt_prop_glob_gov_pow <- ggplot(na.omit(joined_data[, c("prop_global", "gov_pow")]),aes(x = as.factor(gov_pow), y = prop_global)) +
  geom_boxplot() +
  labs(title = "Global proportion of all posts by Government Power",
       x = "Government Power",
       y = "Proportion of global posts") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
#ggsave("Prop_glob_gov_pow.jpg", plot = plt_prop_glob_gov_pow, bg="white")
plt_prop_glob_gov_pow
```

Regional Autonomy
```{r}
plt_prop_glob_reg_auton <- ggplot(na.omit(joined_data[, c("prop_global", "reg_autonom")]),aes(x = as.factor(reg_autonom), y = prop_global)) +
  geom_boxplot() +
  labs(title = "Global proportion of all posts by Regional Autonomy",
       x = "Regional Autonomy",
       y = "Proportion of global posts") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
#ggsave("Prop_glob_reg_autonom.jpg", plot = plt_prop_glob_reg_auton, bg="white")
plt_prop_glob_reg_auton
```

Separatism / Irridentism
```{r}
plt_prop_glob_sep_irred <- ggplot(na.omit(joined_data[, c("prop_global", "sep_irred")]),aes(x = as.factor(sep_irred), y = prop_global)) +
  geom_boxplot() +
  labs(title = "Global proportion of all posts by Separatism / Irridentism",
       x = "Separatism / Irridentism",
       y = "Proportion of global posts") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
#ggsave("Prop_glob_sep_irred.jpg", plot = plt_prop_glob_sep_irred, bg="white")
plt_prop_glob_sep_irred
```


Ethnic Claim
```{r}
plt_prop_glob_eth_claim <- ggplot(na.omit(joined_data[, c("prop_global", "eth_claim")]),aes(x = as.factor(eth_claim), y = prop_global)) +
  geom_boxplot() +
  labs(title = "Global proportion of all posts by Ethnic Claim",
       x = "Ethnic Claim",
       y = "Proportion of global posts") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
#ggsave("Prop_glob_eth_claim.jpg", plot = plt_prop_glob_eth_claim, bg="white")
plt_prop_glob_eth_claim
```


War history (Count variable indicating number of conflict onsets this group has previously experienced)
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plt_glob_prop_war_hist <- ggplot(joined_data, aes(x = warhist, y = prop_global)) +
  geom_jitter() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Proportion of Global Posts by War History",
       x = "War History",
       y = "Proportion of global posts") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
#ggsave("Glob_Prop_war_hist.jpg", plot = plt_glob_prop_war_hist, bg="white")
plt_glob_prop_war_hist
```


VARIABLEN FÜR WEITERE PLOTS:
- primary -> mit allen global/Cntry vars ==> done for: prop_glob
- elect_part -> mit allen global/Cntry vars ==> done for: prop_glob
- gwgroupid -> mit allen (müsste auf gruppenebnen noch aggregiert werden)
- n_epr_grps_cntry -> ist alle gruppen in einem land??? => evtl. alles (müsste auf gruppenebnen noch aggregiert werden)
- language_pred ==> done for: prop_glob
- ed_language1==> done for: prop_glob
- statusname ==> done for: prop_glob
- gov_pow ==> done for: prop_glob
- reg_autonom ==> done for: prop_glob
- sep_irred ==> done for: prop_glob
- eth_claim ==> done for: prop_glob
- warhist ==> müsste auf gruppenebnen noch aggregiert werden
- peaceyears ==> müsste auf gruppenebnen noch aggregiert werden
- onset_ko_flag ==> müsste auf gruppenebnen noch aggregiert werden
- onset_do_flag ==> müsste auf gruppenebnen noch aggregiert werden
- incidence_flag ==> müsste auf gruppenebnen noch aggregiert werden



### Regressions  

#### Global Max Models: multiethnic flag  

DV: global_max & country_max & global with Fixed effects & Clustered Errors
\hfill\break
```{r, include=FALSE}
#Ideas for future: 
#- global~length (whether a certain length of the post is correlated with the choice
#of global or national topics -> perhaps needs mediators)
#- add fixed effects for regions
```

##### Multiethnic Flag and Global Max:     
\hfill\break
This analysis deals with the question whether multiethnic organisations are 
more inclined to have a conversation about global topics.

```{r, echo=FALSE, results="asis", warning=FALSE}
model_global_max_multethn_flag <- felm(global_max ~ multiethnic_flag| gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_global_max_multethn_flag, type="latex", title="Regression Results for Global Max by Multiethnic Flag", style="default", single.row=TRUE, digits=3)
```  

Interpretation: Messages from multiethnic organizations are significantly more likely to discuss global topics.


#### Country Max Models

##### Electoral Participation and Country Max:    
\hfill\break
This analysis is about if electoral participation of an organisation leads to 
more discussions on a national level.

```{r, echo=FALSE, results="asis", warning=FALSE}
model_cntry_max_elect_part <- felm(country_max ~ elect_part | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_cntry_max_elect_part, type="latex", title="Regression Results for Country Max by Electoral Participation", style="default", single.row=TRUE, digits=3)
```  

Interpretation: The effect of electoral participation is not significant.

##### Static exclusion status and Country Max:    
\hfill\break
Here we try to find the impact of an exclusionary status of an organsiation on 
the nationalness of organisations' posts.  

```{r, echo=FALSE, results="asis", warning=FALSE}
model_cntry_max_status_excl_epr_static <- felm(country_max ~ status_excl_epr_static | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_cntry_max_status_excl_epr_static, type="latex", title="Regression Results for Country Max by Exclusionary Status", style="default", single.row=TRUE, digits=3)
```  

Interpretation: Not significant; Maybe could do a model with the exclusion status per year as well (data needs 
to be grouped beforehand)


#### Global Models


##### Country and Global:   


Here, we check whether posts within a country are more focussed on national or 
global topics.
\hfill\break
```{r, eval=FALSE, include=FALSE}
#Disclaimer: Only with year fixed effects; otherwise potential collinearity issues. 
```
\hfill\break
```{r, echo=FALSE, results="asis", warning=FALSE}
model_global_gwidx <- felm(global ~ as.factor(gwid.x) | year| 0 | year, data = joined_data)
stargazer(model_global_gwidx, type="latex", title="Regression Results for Global by Country", style="default", single.row=TRUE, digits=3)
```  

Interpretation: Some countries show a significant effect on whether the conversation is global or national, 
albeit it is only a moderate effect.

##### Organisation age and Global:   
\hfill\break
This statistical model checks whether topics in posts of organisations become 
rather national or global with rising age of the organisations.  

```{r, echo=FALSE, results="asis", warning=FALSE}
model_global_org_age <- felm(global ~ org_age | gwid.x + year | 0 |  gwid.x +year, data = joined_data)
stargazer(model_global_org_age, type="latex", title="Regression Results for Global by Organisation Age", style="default", single.row=TRUE, digits=3)
```  

Interpretation: The age of an organisation has a slightly significant and moderately negative effect on the 
choice of global issues in the discourse.

##### Static exclusion status and Global:  
\hfill\break
This model investigates whether the exclusion status of an organisation influences
whether the conversation is global or national.
```{r, echo=FALSE, results="asis", warning=FALSE}
model_global_status_excl_epr_static <- felm(global ~ status_excl_epr_static | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_global_status_excl_epr_static, type="latex", title="Regression Results for Global by Exclusion Status", style="default", single.row=TRUE, digits=3)
```

Interpretation: The model is not significant.

##### Education language and Global:  
\hfill\break
This analysis examines whether the language in education influences whether the 
posts of organisations are global or national.

```{r, echo=FALSE, results="asis", warning=FALSE}
model_global_ed_language1 <- felm(global ~ ed_language1 | gwid.x +year | 0 | gwid.x +year, data = joined_data)
stargazer(model_global_ed_language1, type="latex", title="Regression Results for Global by Education Language", style="default", single.row=TRUE, digits=3)
```

Interpretation: The language in education has a significant impact on whether the conversation is rather global 
or national.  
Disclaimer: Collinearity issues detected



