---
title: "Analysis of Global and Country Max & Global Variables"
author: "Nathalie Guibert"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    keep_tex: true
    number_sections: true
    latex_engine: xelatex
---


# Analysis file

## Setup is being executed.
```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, tidy.opts = list(width.cutoff = 30), tidy = TRUE)

# Load necessary libraries
library("lfe")
library("ggplot2")
library("countrycode")
library("readr")
library("dplyr")
library("fixest")

# Set working directory
setwd("C:/Users/whatt/Desktop/2024_ResAss_UZHIPZ_WeidmannDonnay/work24DonnayWeidmann/data")

# Load the data
joined_data <- read_csv("joined_data.csv")

# Add country name and region for future fixed effects
joined_data$country_name <- countrycode(joined_data$gwid.x, "gwn", "country.name")
joined_data$region <- countrycode(joined_data$gwid.x, "gwn", "region")

# can be ignored later on
joined_data <- joined_data %>%
  rename(elect_part = "Electoral participation")
```

## Version 1: Current Version

### Regressions

#### Global Max Models: channel type, language prediction, multiethnic flag
DV: global_max & country_max & global with Fixed effects & Clustered Errors
Ideas for future: 
- global~length (ob eine gewisse Länge eher dafür spricht globale/nationale Themen anzusprechen-> braucht man aber Mediatoren)
- add fixed effects for regions

##### Channel Type and Global Max: Does the platform influence how global the conversation is? 
```{r, echo =FALSE, error=TRUE, warning=FALSE, message=FALSE}
model_global_max_channel_type <- felm(global_max ~ as.factor(channel_type) | gwid.x + year | 0 | gwid.x + year, data = joined_data)
summary(model_global_max_channel_type)
```
Interpretation: This model assesses whether the platform influences the globality of the conversation. However, it is currently not working due to a single platform in the dataset.

##### Language Prediction and Global Max: How does the choice of language in the messages affect the globality of the discussions?
```{r, echo=FALSE, warning=FALSE, message=FALSE}
model_global_max_lang_pred <- felm(global_max ~ as.factor(language_pred)  | gwid.x + year | 0 | gwid.x + year, data = joined_data)
summary(model_global_max_lang_pred)
```
Interpretation: The predicted language has a significant, though moderate, impact on global_max, indicating that some languages are better predictors of global topic probabilities.

##### Multiethnic Flag and Global Max: Are multiethnic organisations more inclined to have a conversation about global topics?
```{r, echo=FALSE, warning=FALSE, message=FALSE}
model_global_max_multethn_flag <- felm(global_max ~ multiethnic_flag| gwid.x + year | 0 | gwid.x + year, data = joined_data)
summary(model_global_max_multethn_flag)
```
Interpretation: Messages from multiethnic organizations are significantly more likely to discuss global topics.


#### Country Max Models

##### Language Prediction and Country Max: How does the choice of language in the messages affect the nationwide scope of the discussions?
```{r, echo=FALSE, warning=FALSE, message=FALSE}
model_cntry_max_lang_pred <- felm(country_max ~ as.factor(language_pred) | gwid.x + year | 0 | gwid.x + year, data = joined_data)
summary(model_cntry_max_lang_pred)
```
Interpretation: Similar results as global_max were observed for language prediction.

##### Channel type and Country Max: Does the platform influence how national the conversation is? 
```{r, echo=FALSE, error=TRUE, warning=FALSE, message=FALSE}
model_cntry_max_channel_type <- felm(country_max ~ as.factor(channel_type) | gwid.x + year | 0 | gwid.x + year, data = joined_data)
summary(model_cntry_max_channel_type)
```
Interpretation: Not working due to a single platform in the dataset.

##### Electoral Participation and Country Max: Does the electoral participation of an organisation lead to more discussions on a national level?
```{r, echo=FALSE, warning=FALSE, message=FALSE}
model_cntry_max_elect_part <- felm(country_max ~ elect_part | gwid.x + year | 0 | gwid.x + year, data = joined_data)
summary(model_cntry_max_elect_part)
```
Interpretation: The effect of electoral participation is not significant.

##### Static exclusion status and Country Max: Does the status (exclusion) influence how national a conversation of an organisation is?
```{r, echo=FALSE, warning=FALSE, message=FALSE}
model_cntry_max_status_excl_epr_static <- felm(country_max ~ status_excl_epr_static | gwid.x + year | 0 | gwid.x + year, data = joined_data)
summary(model_cntry_max_status_excl_epr_static)
```
Interpretation: Not significant; Maybe could do a model with the exclusion status per year as well (data needs to be grouped beforehand)


#### Global Models

##### Channel Type and Global: Does the platform influence the choice between global and national topics in posts? 
```{r, echo=FALSE, error=TRUE, warning=FALSE, message=FALSE}
model_global_channel_type <- feglm(global ~ as.factor(channel_type) | gwid.x + year, family=binomial(link="logit"), data = joined_data)
summary(model_global_channel_type)
```
Interpretation: This model aims to understand the influence of the platform on global conversations but is currently not working due to limited data variability in channel types.

##### Country and Global: Is the conversation within a country more focussed on national or global topics?
Disclaimer: Only with year fixed effects; otherwise potential collinearity issues. 
```{r, echo=FALSE, warning=FALSE, message=FALSE}
model_global_gwidx <- feglm(global ~ as.factor(gwid.x) | year, family=binomial(link="logit"), data = joined_data)
summary(model_global_gwidx)
```
Interpretation: Some countries show a significant effect on whether the conversation is global or national, albeit it is only a moderate effect.

##### Organisation age and Global: Do topics become rather national or global with rising age of organisations?
```{r, echo=FALSE, warning=FALSE, message=FALSE}
model_global_org_age <- feglm(global ~ org_age | gwid.x +year, family=binomial(link="logit"), data = joined_data)
summary(model_global_org_age)
```
Interpretation: The age of an organisation has a slightly significant and moderately negative effect on the choice of global issues in the discourse.

##### Static exclusion status and Global: Does the static exclusion status influence whether the conversation is global or national? 
```{r, echo=FALSE, warning=FALSE, message=FALSE}
model_global_status_excl_epr_static <- feglm(global ~ status_excl_epr_static | gwid.x +year, family=binomial(link="logit"), data = joined_data)
summary(model_global_status_excl_epr_static)
```
Interpretation: The model is not significant.

##### Education language and Global: Does the language in education influence whether the conversation is global or national?
```{r, echo=FALSE, warning=FALSE, message=FALSE}
model_global_ed_language1 <- feglm(global ~ ed_language1 | gwid.x +year, family=binomial(link="logit"), data = joined_data)
summary(model_global_ed_language1)
```
Interpretation: The language in education has a significant impact on whether the conversation is rather global or national.
Disclaimer: Collinearity issues detected



### Plots

#### Global / Country Max plots

##### Country

###### Global Max by Country
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plt_globalmax_cntry <- ggplot(joined_data, aes(x = as.factor(gwid.x), y = global_max)) +
  geom_boxplot() +
  labs(title = "Global Max by Country",
       x = "Country",
       y = "Global Max") +
  theme_minimal()
ggsave("Global_Max_Country.jpg", plot = plt_globalmax_cntry, bg="white")
plt_globalmax_cntry
```
Interpretation: The probability of having global conversations varies widely between countries but for most countries the probability is relatively low.


###### Global Max by Country
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plt_cntrymax_cntry <- ggplot(joined_data, aes(x = as.factor(gwid.x), y = country_max)) +
  geom_boxplot() +
  labs(title = "Country Max by Country",
       x = "Country",
       y = "Country Max") +
  theme_minimal()
ggsave("Country_Max_Country.jpg", plot = plt_cntrymax_cntry, bg="white")
plt_cntrymax_cntry
```
Interpretation: The probability of having national conversations stays for the bigger part in most countries below a half.


##### Channel Type

###### Global Max by Channel Type
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plt_globalmax_channel_type <- ggplot(joined_data, aes(x = as.factor(channel_type), y = global_max)) +
  geom_boxplot() +
  labs(title = "Global Max by Channel Type",
       x = "Channel Type",
       y = "Global Max") +
  theme_minimal()
ggsave("Global_Max_Channel_Type.jpg", plot = plt_globalmax_channel_type, bg="white")
plt_globalmax_channel_type
```
Interpretation: This plot is currently not really pertinent, as only one platform has been registered in the data.

###### Country Max by Channel Type
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plt_cntrymax_channel_type <- ggplot(joined_data, aes(x = as.factor(channel_type), y = country_max)) +
  geom_boxplot() +
  labs(title = "Country Max by Channel Type",
       x = "Channel Type",
       y = "Country Max") +
  theme_minimal()
ggsave("Country_Max_Channel_Type.jpg", plot = plt_cntrymax_channel_type, bg="white")
plt_cntrymax_channel_type
```
Interpretation: This plot is currently not really pertinent, as only one platform has been registered in the data.

##### Multiethnic flag

###### Global Max by Multiethnicity flag
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plt_globalmax_multiethnicity <- ggplot(joined_data, aes(x = as.factor(multiethnic_flag), y = global_max)) +
  geom_boxplot() +
  labs(title = "Global Max by Multiethnicity",
       x = "Multiethnicity",
       y = "Global Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal()
ggsave("Global_Max_Multiethnicity.jpg", plot = plt_globalmax_multiethnicity, bg="white")
plt_globalmax_multiethnicity
```
Interpretation: If the organisation is multiethnic, the conversations are basically all global, whereas when the organisation isn't multiethnic, the conversation has a tendency to not be global but with many outliers.

###### Country Max by Multiethnicity flag
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plt_cntrymax_multiethnicity <- ggplot(joined_data, aes(x = as.factor(multiethnic_flag), y = country_max)) +
  geom_boxplot() +
  labs(title = "Country Max by Multiethnicity",
       x = "Multiethnicity",
       y = "Country Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal()
ggsave("Country_Max_Multiethnicity.jpg", plot = plt_cntrymax_multiethnicity, bg="white")
plt_cntrymax_multiethnicity
```
Interpretation: Independent of the multiethnicity of organisations, the conversations have a lower probability to be about national topics, albeit when the organisation is not multiethnic there are also many outliers that the conversation is indeed rather focussed on national issues.

##### Organisation Age
Disclaimer: I am not happy with how these plots look like yet.
Idea: Perhaps box plots for global and then group the organisation age by 10 years.

###### Global Max by Organisation age
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plt_globalmax_org_age <- ggplot(joined_data, aes(x = org_age, y = global_max)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Global Max by Organization Age",
       x = "Organization Age",
       y = "Global Max") +
  theme_minimal()
ggsave("Global_Max_Org_Age.jpg", plot = plt_globalmax_org_age, bg="white")
plt_globalmax_org_age
```
Interpretation: In the plot is a slight tendency that with growing age posts become more likely to be global, however, the data points are too randomly distributed to make a general assumption.

###### Country Max by Organisation age
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plt_cntrymax_org_age <- ggplot(joined_data, aes(x = org_age, y = country_max)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Country Max by Organization Age",
       x = "Organization Age",
       y = "Country Max") +
  theme_minimal()
ggsave("Country_Max_Org_Age.jpg", plot = plt_cntrymax_org_age, bg="white")
plt_cntrymax_org_age
```
Interpretation: Same as above, only the tendency to be more nation-minded is slightly higher.


##### Static exclusion status

###### Global Max by Static exclusion status
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plt_globalmax_static_excl <- ggplot(na.omit(joined_data[, c("global_max", "status_excl_epr_static")]), aes(x = as.factor(status_excl_epr_static), y = global_max)) +
  geom_boxplot() +
  labs(title = "Global Max by Static Exclusion Status",
       x = "Static Exclusion Status",
       y = "Global Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal()
ggsave("Global_Max_static_exclusion.jpg", plot = plt_globalmax_static_excl, bg="white")
plt_globalmax_static_excl
```
Interpretation: The probability of having global posts is for both excluded and included organisations relatively low, albeit there are many outliers in both cases.

###### Country Max by Static exclusion status
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plt_cntrymax_static_excl <- ggplot(na.omit(joined_data[, c("global_max", "status_excl_epr_static")]), aes(x = as.factor(status_excl_epr_static), y = global_max)) +
  geom_boxplot() +
  labs(title = "Country Max by Static Exclusion Status",
       x = "Static Exclusion Status",
       y = "Country Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal()
ggsave("Country_Max_static_exclusion.jpg", plot = plt_cntrymax_static_excl, bg="white")
plt_cntrymax_static_excl
```
Interpretation: Same result as above is applicable to the probability of having posts focussed on country issues. Thus, I would argue that the status of an organisation does neither explain the likelihood of globality of posts nor the likelihood of a nation-focus of posts.

Disclaimer: Plots for global variable, as well as exclusion status per year are a work in process.
