---
title: "Analysis of Global and Country Max & Global Variables"
author: "Nathalie Guibert"
date: "`r Sys.Date()`"
output: pdf_document
---

# Analysis file


## Setup is being executed.

```{r setup, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
knitr::opts_chunk$set(message = FALSE, tidy.opts = list(width.cutoff = 30), tidy = TRUE)
knitr::opts_chunk$set(fig.width=6, fig.height=4)
knitr::opts_chunk$set(error=TRUE)

# Load necessary libraries
library("lfe")
library("ggplot2")
library("ggExtra")
library("countrycode")
library("readr")
library("dplyr")
library("fixest")
library("texreg")
library("texreg")
library("formatR")
library("stargazer")

# Set working directory
setwd("C:/Users/whatt/Desktop/2024_ResAss_UZHIPZ_WeidmannDonnay/work24DonnayWeidmann/data")

# Load the data
joined_data <- read_csv("joined_data.csv")

# Add country name and region for future fixed effects
joined_data$country_name <- countrycode(joined_data$gwid.x, "gwn", "country.name")
joined_data$region <- countrycode(joined_data$gwid.x, "gwn", "region")

```

\hfill\break
### Plots

#### Global / Country Max plots; Goal: Compare Global and Country Orientation of Posts

##### Compare global_max scores and country_max scores based on posts    
\hfill\break
Here we would like to see if organisations tend to communicate more on a global or national 
level by comparing their global_max and country_max scores (both metrics measure 
the likelihood of content being about global or national topics).
Here we compare global_max scores and country_max scores using a regression line to detect
a correlation; as one of those two dimensions for a post should be higher as the 
other one, as we would expect that an organisation communicates either rather on 
a global or on a country level.

```{r, error=FALSE}
plt_global_country_max <- ggplot(joined_data, aes(x = global_max, y = country_max)) +
  geom_point(alpha = 0.6) +  
  geom_smooth(method = "lm", col = "blue", se = FALSE) +   
  labs(title = "Global Max vs Country Max",
       x = "Global Max",
       y = "Country Max") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -2),
    axis.title.y = element_text(vjust = 2)
  ) 

ggExtra::ggMarginal(plt_global_country_max, size = 2,type = "histogram", xparams= list(fill="lightblue"), yparams =list(fill="lightgreen"))

ggsave("global_country_max_scatter.jpg", plot= plt_global_country_max, bg = "white")
 
  
```

Same but posts divided in regions.

```{r, include=FALSE}
plt_global_country_max_regions <- ggplot(joined_data, aes(x = global_max, y = country_max, colour=region)) +
  geom_point(alpha = 0.5) +  
  geom_smooth(method = "lm", col = "black", se = FALSE) +  
  labs(title = "Scatterplot: Global Max vs Country Max",
       x = "Global Max",
       y = "Country Max") +
  theme_minimal() 

ggExtra::ggMarginal(plt_global_country_max_regions, groupColour = TRUE, groupFill = TRUE)

ggsave("global_country_max_regions.jpg", plot= plt_global_country_max_regions, bg = "white")
```

Contrary to our assumption, the plot indicates a positive correlation between
country_max and global_max scores, thus, implying that if the global max score is 
higher, then also the country max score is higher. Thus, this may mean that posts 
that generally have a relation to a geographical level will spur up scores on both
country and global level. Disclaimer: These preliminary results should be used 
with caution: Currently there is a data issue which maps these scores to the wrong
posts in another dataset. Furthermore, it should also be mentioned that there 
are many posts with a zero score on a country level, whereas zero scores barely
exist for the global scores.

\hfill\break
##### Country  
\hfill\break
Global Max by Country  

Here we assess how the likelihood of global conversations varies across different countries.

```{r,  warning=FALSE, message=FALSE}
plt_globalmax_cntry <- ggplot(joined_data, aes(x = as.factor(country_name), y = global_max)) +
  geom_boxplot(fill = "lightblue", color = "black") +  
  labs(title = "Global Max by Country",
       x = "Country",
       y = "Global Max") +  
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45), 
        axis.title.y = element_text(vjust = 0.5),
        legend.position = "none") 

ggsave("Global_Max_Country.jpg", plot = plt_globalmax_cntry, bg="white")
plt_globalmax_cntry
```  

Interpretation: The probability of having global conversations varies widely 
between countries but for most countries the probability is relatively low.

\hfill\break
Country Max by Country  

Here we assess how the likelihood of national conversations varies across different countries.

```{r,  warning=FALSE, message=FALSE}
plt_cntrymax_cntry <- ggplot(joined_data, aes(x = as.factor(country_name), y = country_max)) +
  geom_boxplot(fill = "lightgreen", color="black") +
  labs(title = "Country Max by Country",
       x = "Country",
       y = "Country Max") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45), 
        axis.title.y = element_text(vjust = 0.5),
        legend.position = "none") 
ggsave("Country_Max_Country.jpg", plot = plt_cntrymax_cntry, bg="white")
plt_cntrymax_cntry
```

Interpretation: The probability of having national conversations stays for the bigger part in most countries 
below a half.

\hfill\break
##### Channel Type  
\hfill\break
Here, we check whether the type of channel has an impact of the globality and
nationalistic of the posts.

Global Max by Channel Type

```{r,  warning=FALSE, message=FALSE}
plt_globalmax_channel_type <- ggplot(joined_data, aes(x = as.factor(channel_type), y = global_max)) +
  geom_boxplot() +
  labs(title = "Global Max by Channel Type",
       x = "Channel Type",
       y = "Global Max") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Global_Max_Channel_Type.jpg", plot = plt_globalmax_channel_type, bg="white")
plt_globalmax_channel_type
```  

Interpretation: This plot is currently not really pertinent, as only one platform has been registered in the 
data.

\hfill\break
Country Max by Channel Type 

```{r,  warning=FALSE, message=FALSE}
plt_cntrymax_channel_type <- ggplot(joined_data, aes(x = as.factor(channel_type), y = country_max)) +
  geom_boxplot() +
  labs(title = "Country Max by Channel Type",
       x = "Channel Type",
       y = "Country Max") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Country_Max_Channel_Type.jpg", plot = plt_cntrymax_channel_type, bg="white")
plt_cntrymax_channel_type
```

Interpretation: This plot is currently not really pertinent, as only one platform has been registered in the 
data.

\hfill\break
##### Multiethnic flag  
\hfill\break
Here, we examine whether an organisation's status as multiethnic influences the
global or national focus of its posts.  

Global Max by Multiethnicity flag

```{r,  warning=FALSE, message=FALSE}
plt_globalmax_multiethnicity <- ggplot(joined_data, aes(x = as.factor(multiethnic_flag), y = global_max)) +
  geom_boxplot() +
  labs(title = "Global Max by Multiethnicity",
       x = "Multiethnicity",
       y = "Global Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Global_Max_Multiethnicity.jpg", plot = plt_globalmax_multiethnicity, bg="white")
plt_globalmax_multiethnicity
```  

Interpretation: If the organisation is multiethnic, the conversations are basically all global, whereas when the
organisation isn't multiethnic, the conversation has a tendency to not be global but with many outliers.

\hfill\break
Country Max by Multiethnicity flag

```{r,  warning=FALSE, message=FALSE}
plt_cntrymax_multiethnicity <- ggplot(joined_data, aes(x = as.factor(multiethnic_flag), y = country_max)) +
  geom_boxplot() +
  labs(title = "Country Max by Multiethnicity",
       x = "Multiethnicity",
       y = "Country Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() + 
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Country_Max_Multiethnicity.jpg", plot = plt_cntrymax_multiethnicity, bg="white")
plt_cntrymax_multiethnicity
```  

Interpretation: Independent of the multiethnicity of organisations, the conversations have a lower probability 
to be about national topics, albeit when the organisation is not multiethnic there are also many outliers that 
the conversation is indeed rather focussed on national issues.

\hfill\break
##### Organisation Age  
\hfill\break
Here, we examine whether an organisation's age has an impact on the global or national 
focus of its posts.  

Global Max by Organisation age

```{r,  warning=FALSE, message=FALSE}
plt_globalmax_org_age <- ggplot(joined_data, aes(x = org_age, y = global_max)) +
  geom_jitter() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Global Max by Organization Age",
       x = "Organization Age",
       y = "Global Max") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Global_Max_Org_Age.jpg", plot = plt_globalmax_org_age, bg="white")
plt_globalmax_org_age
```  

Interpretation: In the plot is a slight tendency that with growing age posts become more likely to be global, 
however, the data points are too randomly distributed to make a general assumption.

\hfill\break
Country Max by Organisation age

```{r,  warning=FALSE, message=FALSE}
plt_cntrymax_org_age <- ggplot(joined_data, aes(x = org_age, y = country_max)) +
  geom_jitter() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Country Max by Organization Age",
       x = "Organization Age",
       y = "Country Max") +
  theme_minimal() + 
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Country_Max_Org_Age.jpg", plot = plt_cntrymax_org_age, bg="white")
plt_cntrymax_org_age
```  

Interpretation: Same as above, only the tendency to be more national-minded is slightly higher.

\hfill\break
##### Static exclusion status   
\hfill\break
In these plots, we check whether an exclusionary status of the organisation has
an impact on the globality and nationalistic of a organisation's posts.  

Global Max by Static exclusion status

```{r,  warning=FALSE, message=FALSE}
plt_globalmax_static_excl <- ggplot(na.omit(joined_data[, c("global_max", "status_excl_epr_static")]), aes(x = as.factor(status_excl_epr_static), y = global_max)) +
  geom_boxplot() +
  labs(title = "Global Max by Static Exclusion Status",
       x = "Static Exclusion Status",
       y = "Global Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Global_Max_static_exclusion.jpg", plot = plt_globalmax_static_excl, bg="white")
plt_globalmax_static_excl
```

Interpretation: The probability of having global posts is for both excluded and included organisations 
relatively low, albeit there are many outliers in both cases.

\hfill\break
Country Max by Static exclusion status  

```{r,  warning=FALSE, message=FALSE}
plt_cntrymax_static_excl <- ggplot(na.omit(joined_data[, c("country_max", "status_excl_epr_static")]), aes(x = as.factor(status_excl_epr_static), y = country_max)) +
  geom_boxplot() +
  labs(title = "Country Max by Static Exclusion Status",
       x = "Static Exclusion Status",
       y = "Country Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -2),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Country_Max_static_exclusion.jpg", plot = plt_cntrymax_static_excl, bg="white")
plt_cntrymax_static_excl
```

Interpretation: Same result as above is applicable to the probability of having posts focussed on country 
issues. Thus, I would argue that the status of an organisation does neither explain the likelihood of globality 
of posts nor the likelihood of a nation-focus of posts.

\hfill\break
#### Adding of variables from "new" datasets (EPR, Conflict and Power datasets)

##### Global Max & Country Max
\hfill\break
###### By Primary channel

Here, I check whether the usage of a specific platform as primary channel of 
an organisation affects the probability of organisations having global or national 
online conversation.

```{r}
plt_globmax_prim_chan <- ggplot(na.omit(joined_data[, c("global_max", "primary")]), aes(x = as.factor(primary), y = global_max)) +
  geom_boxplot() +
  labs(title = "Global Max by Primary Channel",
       x = "Primary Channel",
       y = "Global Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Global_Max_primary.jpg", plot = plt_globmax_prim_chan, bg="white")
plt_globmax_prim_chan
```

Interpretation: In the current dataset, there is no data variation as to whether a channel is the
primary way of communication or not; for all current data points (for which the 
respective channel is not a primary account), the probability of the conversation 
being global is relatively low. 

\hfill\break
Country Max by Primary Channel

```{r}
plt_cntrymax_prim_chan <- ggplot(na.omit(joined_data[, c("country_max", "primary")]), aes(x = as.factor(primary), y = country_max)) +
  geom_boxplot() +
  labs(title = "Country Max by Primary Channel",
       x = "Primary Channel",
       y = "Country Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Country_Max_primary.jpg", plot = plt_cntrymax_prim_chan, bg="white")
plt_cntrymax_prim_chan
```

Interpretation: Same as above applies here; for all current data points (for which the 
respective channel is not a primary account), the probability of the conversation 
being national is relatively low. 


###### By Electoral Participation
\hfill\break
Global Max by Electoral Participation

Here, I check whether the electoral participation of an organisation affects the 
probability of organisations having global or national online conversation.

```{r}
plt_globmax_elect_part <- ggplot(na.omit(joined_data[, c("global_max", "elect_part")]), aes(x = as.factor(elect_part), y = global_max)) +
  geom_boxplot() +
  labs(title = "Global Max by Electoral Participation",
       x = "Electoral Participation",
       y = "Global Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Global_Max_elect_part.jpg", plot = plt_globmax_elect_part, bg="white")
plt_globmax_elect_part
```

Interpretation: There seems to be barely any obvious impact of an organisation's 
electoral participation on whether their communication is more likely to be global 
or not.

\hfill\break
Country Max by Electoral Participation

```{r}
plt_cntrymax_elect_part <- ggplot(na.omit(joined_data[, c("country_max", "elect_part")]), aes(x = as.factor(elect_part), y = country_max)) +
  geom_boxplot() +
  labs(title = "Country Max by Electoral Participation",
       x = "Electoral Participation",
       y = "Country Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Country_Max_elect_part.jpg", plot = plt_cntrymax_elect_part, bg="white")
plt_cntrymax_elect_part
```

Interpretation: There seems to be barely any obvious impact of an organisation's 
electoral participation on whether their communication is more likely to be 
national or not.


###### By Language Prediction
\hfill\break
Global Max by Language Prediction

Here, I check whether the language that an organisation uses in their 
communication affects the probability of organisations having global or national 
online conversation.

```{r}
plt_globmax_lang_pred <- ggplot(joined_data, aes(x = as.factor(language_pred), y = global_max)) +
  geom_boxplot(fill = "lightgreen", color="black") +
  labs(title = "Global Max by Language Prediction",
       x = "Language Prediction",
       y = "Global Max") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45), 
        axis.title.y = element_text(vjust = 0.5),
        legend.position = "none") 

ggsave("Global_Max_lang_pred.jpg", plot = plt_globmax_lang_pred, bg="white", width = 20, height = 8, units = "cm")

plt_globmax_lang_pred
```

Interpretation: The language tends only to slightly influence the probability of 
the organisations having a global discourse. Only in the cases of the language
Czech, as well as also less strong in the cases of Asturianu, Finnish, and Portuguese
language may be seen as a driver of a more global conversation.

\hfill\break
Country Max by Language Prediction

```{r}
plt_cntrymax_lang_pred <- ggplot(joined_data, aes(x = as.factor(language_pred), y = country_max)) +
  geom_boxplot(fill = "lightgreen", color="black") +
  labs(title = "Country Max by Language Prediction",
       x = "Language Prediction",
       y = "Country Max") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45), 
        axis.title.y = element_text(vjust = 0.5),
        legend.position = "none") 

ggsave("Cntry_Max_lang_pred.jpg", plot = plt_cntrymax_lang_pred, bg="white", width = 20, height = 8, units = "cm")

plt_cntrymax_lang_pred
```

Interpretation: Tendencial, it seems like the language has a greater impact on 
the organisations' communication being more national-minded compared to the 
probability of having more global conversations. Interesting data points here are:
Turkish seems to be particularly drive a more national conversation, as well as 
Norwegian, Asturian, and Czech.

###### By Education Language
\hfill\break
Global Max by Education Language 

Here, I check whether the education language used by an organisation in a given 
country affects the probability of organisations having global or national 
online conversation.

```{r}
plt_globmax_educ_lang <- ggplot(na.omit(joined_data[, c("global_max", "ed_language1")]), aes(x = as.factor(ed_language1), y = global_max)) +
  geom_boxplot(fill = "lightgreen", color="black") +
  labs(title = "Global Max by Education Language",
       x = "Education Language",
       y = "Global Max") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45), 
        axis.title.y = element_text(vjust = 0.5),
        legend.position = "none") 

ggsave("Global_Max_educ_lang.jpg", plot = plt_globmax_educ_lang, bg="white", width = 20, height = 8, units = "cm")

plt_globmax_educ_lang
```

Interpretation: Tendentially, the language of education seems to influence 
whether an organisation's communication is more likely to be global. This is 
particularly true for Chavacano, Welsh, and Quechua.

\hfill\break
Country Max by Education Language 

```{r}
plt_cntrymax_educ_lang <- ggplot(na.omit(joined_data[, c("country_max", "ed_language1")]), aes(x = as.factor(ed_language1), y = country_max)) +
  geom_boxplot(fill = "lightgreen", color="black") +
  labs(title = "Country Max by Education Language",
       x = "Education Language",
       y = "Country Max") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45), 
        axis.title.y = element_text(vjust = 0.5),
        legend.position = "none") 

ggsave("Cntry_Max_educ_lang.jpg", plot = plt_cntrymax_educ_lang, bg="white", width = 20, height = 8, units = "cm")

plt_cntrymax_educ_lang
```

Interpretation: Compared to the likelihood of an organisation's communication
being global, the education language seems to have a slightly less powerful 
impact on the conversation being national, where the general mean stays under 0.5.
Portuguese, Welsh and Quecha seem to be most influential in driving the likelihood
of a more national conversation.

###### By Statusname
\hfill\break
Global Max by statusname

Here, I check whether the status of an organisation in a given country affects 
the probability of organisations having global or national online conversation.

```{r}
plt_globmax_statusname <- ggplot(na.omit(joined_data[, c("global_max", "statusname")]), aes(x = as.factor(statusname), y = global_max)) +
  geom_boxplot(fill = "lightgreen", color="black") +
  labs(title = "Global Max by Statusname",
       x = "Statusname",
       y = "Global Max") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45), 
        axis.title.y = element_text(vjust = 0.5),
        legend.position = "none") 

ggsave("Global_Max_statusname.jpg", plot = plt_globmax_statusname, bg="white")

plt_globmax_statusname
```

Interpretation: The status of an organisation has only a slight impact on the 
the variation of the likelihood to have a global conversation. If an organisation
is discriminated against, the conversation seems to be slightly more likely to 
be global, compared to the other stati.

\hfill\break
Country Max by statusname

```{r}
plt_cntrymax_statusname <- ggplot(na.omit(joined_data[, c("country_max", "statusname")]), aes(x = as.factor(statusname), y = country_max)) +
  geom_boxplot(fill = "lightgreen", color="black") +
  labs(title = "Country Max by Statusname",
       x = "Statusname",
       y = "Country Max") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45), 
        axis.title.y = element_text(vjust = 0.5),
        legend.position = "none") 

ggsave("Cntry_Max_statusname.jpg", plot = plt_cntrymax_statusname, bg="white")

plt_cntrymax_statusname
```

Interpretation: The status of an organisation has an impact on the the variation 
of the likelihood to have a national conversation, especially in the case of an 
organisation being discriminated against. The overall probability of communication
being national stays relatively low in all stati, however. 

###### By Government Power
\hfill\break
Global Max by Government Power

Here, I check whether the government power of an organisation in a given country affects 
the probability of organisations having global or national online conversation.

```{r}
plt_globmax_gov_pow <- ggplot(na.omit(joined_data[, c("global_max", "gov_pow")]), aes(x = as.factor(gov_pow), y = global_max)) +
  geom_boxplot() +
  labs(title = "Global Max by Government Power",
       x = "Government Power",
       y = "Global Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Global_Max_gov_pow.jpg", plot = plt_globmax_gov_pow, bg="white")
plt_globmax_gov_pow
```

Interpretation: There seems to be only a minor difference between the impact of
an organisation having government power on the likelihood of having global conversations.

\hfill\break
Country Max by Government Power

```{r}
plt_cntrymax_gov_pow <- ggplot(na.omit(joined_data[, c("country_max", "gov_pow")]), aes(x = as.factor(gov_pow), y = country_max)) +
  geom_boxplot() +
  labs(title = "Country Max by Government Power",
       x = "Government Power",
       y = "Country Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Cntry_Max_gov_pow.jpg", plot = plt_cntrymax_gov_pow, bg="white")
plt_cntrymax_gov_pow
```

Interpretation: There seems to be only a minor difference between the impact of
an organisation having government power on the likelihood of having national conversations.


###### By Regional Autonomy
\hfill\break
Global Max by Regional Autonomy

Here, I check whether the regional autonomy of an organisation in a given country affects 
the probability of organisations having global or national online conversation.

```{r}
plt_globmax_reg_aut <- ggplot(na.omit(joined_data[, c("global_max", "reg_autonom")]), aes(x = as.factor(reg_autonom), y = global_max)) +
  geom_boxplot() +
  labs(title = "Global Max by Regional Autonomy",
       x = "Regional Autonomy",
       y = "Global Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Global_Max_reg_aut.jpg", plot = plt_globmax_reg_aut, bg="white")
plt_globmax_reg_aut
```

Interpretation: There seems to be only a minor difference between the impact of
an organisation having regional autonomy on the likelihood of having global 
conversations.

\hfill\break
Country Max by Regional Autonomy

```{r}
plt_cntrymax_reg_aut <- ggplot(na.omit(joined_data[, c("country_max", "reg_autonom")]), aes(x = as.factor(reg_autonom), y = country_max)) +
  geom_boxplot() +
  labs(title = "Country Max by Regional Autonomy",
       x = "Regional Autonomy",
       y = "Country Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Cntry_Max_reg_aut.jpg", plot = plt_cntrymax_reg_aut, bg="white")
plt_cntrymax_reg_aut
```

Interpretation: There seems to be only a minor difference between the impact of
an organisation having regional autonomy on the likelihood of having national 
conversations.

###### By Separatism / Irridentism
\hfill\break
Global Max by Separatism / Irridentism

Here, I check whether the separatism or irridentism of an organisation in a given 
country affects the probability of organisations having global or national online 
conversation.

```{r}
plt_globmax_sep_irred <- ggplot(na.omit(joined_data[, c("global_max", "sep_irred")]), aes(x = as.factor(sep_irred), y = global_max)) +
  geom_boxplot() +
  labs(title = "Global Max by Separatism/Irridentism",
       x = "Separatism/Irridentism",
       y = "Global Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Global_Max_sep_irred.jpg", plot = plt_globmax_sep_irred, bg="white")
plt_globmax_sep_irred
```

Interpretation: There seems to be only a minor difference between the impact of
an organisation having separatism/irridentism on the likelihood of having global 
conversations.

\hfill\break
Country Max by Separatism / Irridentism

```{r}
plt_cntrymax_sep_irred <- ggplot(na.omit(joined_data[, c("country_max", "sep_irred")]), aes(x = as.factor(sep_irred), y = country_max)) +
  geom_boxplot() +
  labs(title = "Country Max by Separatism/Irridentism",
       x = "Separatism/Irridentism",
       y = "Country Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Cntry_Max_sep_irred.jpg", plot = plt_cntrymax_sep_irred, bg="white")
plt_cntrymax_sep_irred
```

Interpretation: There seems to be only a minor difference between the impact of
an organisation having separatism/irridentism on the likelihood of having national 
conversations.

###### By Ethnic Claim
\hfill\break
Global Max by Ethnic Claim

Here, I check whether the existence of an ethnic claim of an organisation affects 
the probability of organisations having global or national online conversation.

```{r}
plt_globmax_eth_claim <- ggplot(na.omit(joined_data[, c("global_max", "eth_claim")]), aes(x = as.factor(eth_claim), y = global_max)) +
  geom_boxplot() +
  labs(title = "Global Max by Ethnic Claim",
       x = "Ethnic Claim",
       y = "Global Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Global_Max_eth_claim.jpg", plot = plt_globmax_eth_claim, bg="white")
plt_globmax_eth_claim
```

Interpretation: There seems to be only a minor difference between the impact of
an organisation making use of an ethnic claim on the likelihood of having global 
conversations.

\hfill\break
Country Max by Ethnic Claim

```{r}
plt_cntrymax_eth_claim <- ggplot(na.omit(joined_data[, c("country_max", "eth_claim")]), aes(x = as.factor(eth_claim), y = country_max)) +
  geom_boxplot() +
  labs(title = "Country Max by Ethnic Claim",
       x = "Ethnic Claim",
       y = "Country Max") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
ggsave("Cntry_Max_eth_claim.jpg", plot = plt_cntrymax_eth_claim, bg="white")
plt_cntrymax_eth_claim
```

Interpretation: There seems to be only a minor difference between the impact of
an organisation making use of an ethnic claim on the likelihood of having national 
conversations.

\hfill\break
##### Prop Global (Global Proportion)

\hfill\break
###### Distribution of global post proportions over all organisations

```{r}
unique_organisations <- joined_data %>%
  distinct(org_id_from_coll, .keep_all = TRUE)

prop_of_glob_props <- ggplot(unique_organisations, aes(x = prop_global)) +
  geom_histogram(binwidth = 0.05, fill = "skyblue", color = "black") +
  labs(
    title = "Distribution of Global Post Proportions",
    x = "Proportion of global posts",
    y = "Number of Organisations"
  ) +
  theme_minimal()

ggsave("Proportions_GlobalProportions.jpg", plot = prop_of_glob_props, bg="white")
prop_of_glob_props

```

Interpretation: Most organisations only use global posts. 

\hfill\break
###### Distribution of global post proportions over all countries

```{r}
plt_propglob_cntry <- ggplot(joined_data, aes(x = as.factor(country_name), y = prop_global)) +
  geom_boxplot(fill = "beige", color="black") +
  labs(title = "Proportion of global posts by Country",
       x = "Country",
       y = "Global Proportion") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90), 
        axis.title.y = element_text(vjust = 0.5),
        legend.position = "none") 
#ggsave("Prop_Glob_Country.jpg", plot = plt_propglob_cntry, bg="white")
plt_propglob_cntry
```

Interpretation: As with the organisations, most countries have more global 
conversations (independent of the organisations), except Uruquay. This is 
particularly true for Albania, Bolivia, Ecuador, France, Paraguay and Peru.

\hfill\break
###### Distribution of global post proportions over all regions

```{r}
plt_propglob_region <- ggplot(joined_data, aes(x = as.factor(region), y = prop_global)) +
  geom_boxplot(fill = "beige", color="black") +
  labs(title = "Proportion of global posts by Region",
       x = "Region",
       y = "Global Proportion") +
  theme_minimal() +
  theme(axis.title.y = element_text(vjust = 0.5),
        legend.position = "none") 
#ggsave("Prop_Global_Region.jpg", plot = plt_propglob_region, bg="white")
plt_propglob_region
```

Interpretation: The region with the highest proportion of global posts is Latin
America & Caribbean compared to Europe and Central Asia, where only roughly 40% 
of the conversation is global.
 
\hfill\break
###### Distribution of global post proportions over all channel types

```{r,  warning=FALSE, message=FALSE}
plt_prop_glob_channel_type <- ggplot(joined_data, aes(x = as.factor(channel_type), y = prop_global)) +
  geom_boxplot() +
  labs(title = "Global proportion of all posts by Channel Type",
       x = "Channel Type",
       y = "Proportion of global posts") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
#ggsave("Prop_Global_Channel_Type.jpg", plot = plt_prop_glob_channel_type, bg="white")
plt_prop_glob_channel_type
```  

Interpretation: As there is currently only one channel type ("Facebook"), the 
comparative nature of this graph lacks variability. Overall, for Facebook the 
proportion of global posts is around 35%.

\hfill\break
###### Distribution of global post proportions over whether an organisation is multiethnic or not.

```{r}
plt_prop_glob_multiethnicity <- ggplot(joined_data, aes(x = as.factor(multiethnic_flag), y = prop_global)) +
  geom_boxplot() +
  labs(title = "Global proportion of all posts by Multiethnicity",
       x = "Multiethnicity",
       y = "Proportion of global posts") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
#ggsave("Prop_glob_Multiethnicity.jpg", plot = plt_prop_glob_multiethnicity, bg="white")
plt_prop_glob_multiethnicity
```

Interpretation: If the organisation is multiethnic, then all posts seem to be 
global. This proportion is definitely lower for non-multiethnic organisations at 
35% roughly.

\hfill\break
###### Distribution of global post proportions over growing organisation age with regression line.

```{r}
plt_prop_glob_org_age <- ggplot(joined_data, aes(x = org_age, y = prop_global)) +
  geom_jitter() +
  geom_smooth(method = "lm", se = TRUE) +
  labs(title = "Global proportion of all posts by Organization Age",
       x = "Organization Age",
       y = "Proportion of global posts") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
#ggsave("Prop_Global_Org_Age.jpg", plot = plt_prop_glob_org_age, bg="white")
plt_prop_glob_org_age
```

Interpretation: Over a growing age of an organisation, there is a slight tendency
to have lower proportions of global posts. However, most of the observations
can be observed until the age of 50, and spread widely across the possible 
proportions, thus showing no clear tendency if the organisation is less than 50 
year old.

\hfill\break
###### Distribution of global post proportions over whether an organisation has an exclusion status or not.

```{r}
plt_prop_glob_static_excl <- ggplot(na.omit(joined_data[, c("prop_global", "status_excl_epr_static")]), aes(x = as.factor(status_excl_epr_static), y = prop_global)) +
  geom_boxplot() +
  labs(title = "Global proportion of all posts by Static Exclusion Status",
       x = "Static Exclusion Status",
       y = "Proportion of global posts") +
  scale_x_discrete(labels=c("No", "Yes"))+
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
#ggsave("Prop_glob_static_exclusion.jpg", plot = plt_prop_glob_static_excl, bg="white")
plt_prop_glob_static_excl
```

Interpretation: Organisations which are being excluded tend to slightly use less
global posts than organisation which are not being excluded.

\hfill\break
###### Distribution of global post proportions over whether the used account is a primary account of an organisation or not.

```{r}
plt_prop_glob_primary <- ggplot(joined_data, aes(x = as.factor(primary), y = prop_global)) +
  geom_boxplot() +
  labs(title = "Global proportion of all posts by Primary Account",
       x = "Primary Account",
       y = "Proportion of global posts") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
#ggsave("Prop_Global_Primary.jpg", plot = plt_prop_glob_primary, bg="white")
plt_prop_glob_primary
```

Interpretation: As all the posts are being sent from the organisations' primary
account, such that the comparative nature of this graph lacks variability. 
Overall, the primary accounts' proportion of global posts is around 35%.

\hfill\break
###### Distribution of global post proportions over whether the organisation is participating in elections or not.

```{r}
plt_prop_glob_elect_part <- ggplot(joined_data, aes(x = as.factor(elect_part), y = prop_global)) +
  geom_boxplot() +
  labs(title = "Global proportion of all posts by Electoral Participation of organisation",
       x = "Electoral Participation",
       y = "Proportion of global posts") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
#ggsave("Prop_Global_Elect_Part.jpg", plot = plt_prop_glob_elect_part, bg="white")
plt_prop_glob_elect_part
```

Interpretation: If the organisation is participating in elections, the 
proportion of global posts is around 37%, thus lower than when an organisation
is not participating in elections, with around 55% of all posts being global.

\hfill\break
###### Distribution of global post proportions by predicted language 

```{r, fig.width=10, fig.height=8}
plt_propglob_langpred <- ggplot(joined_data, aes(x = as.factor(language_pred), y = prop_global)) +
  geom_boxplot(fill = "beige", color = "black", position=position_dodge(width=3)) +
  labs(
    title = "Proportion of Global Posts by Language",
    x = "Language",
    y = "Global Proportion"
  ) +
  theme_minimal() +
  theme(axis.title.y = element_text(vjust = 0.5)) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))  # Staggers labels


#ggsave("Prop_Global_Lang.jpg", plot = plt_propglob_langpred, bg="white")
plt_propglob_langpred
```

Interpretation: While the mean of the general global proportions is around 37% 
roughly, the highest proportion of global posts can be found in the Welsh 
language, whereas the lowest within the Bulgarian and Macedonian.

\hfill\break
###### Distribution of global post proportions by used language in education in the country where the respective organisation is located.

```{r, fig.width=10, fig.height=8}
plt_propglob_langeduc <- ggplot(joined_data, aes(x = as.factor(ed_language1), y = prop_global)) +
  geom_boxplot(fill = "beige", color = "black", position=position_dodge(width=3)) +
  labs(
    title = "Proportion of Global Posts by Language in Education",
    x = "Language in education",
    y = "Global Proportion"
  ) +
  theme_minimal() +
  theme(axis.title.y = element_text(vjust = 0.5)) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))  # Staggers labels


#ggsave("Prop_Global_Lang_Educ.jpg", plot = plt_propglob_langeduc, bg="white")
plt_propglob_langeduc
```

Interpretation: There does not seem to be an overall trend of how the proportions
of global posts looks across the languages used in education. Alsatian,
Nivaclé, German, Eastern Punjabi, Quecha, and Cusco Quecha seem to have the
highest proportions of global posts, whereas Bosnian and Romano-Serbian have the lowest
proportions of global posts. 

\hfill\break
###### Distribution of global post proportions by status

```{r}
plt_prop_glob_statusname <- ggplot(joined_data, aes(x = as.factor(statusname), y = prop_global)) +
  geom_boxplot() +
  labs(title = "Global proportion of all posts by status",
       x = "Status",
       y = "Proportion of global posts") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2),
    axis.text.x = element_text(angle = 90)
  ) 
#ggsave("Prop_Global_Status.jpg", plot = plt_prop_glob_statusname, bg="white")
plt_prop_glob_statusname
```

Interpretation: Overall, most of the status drive similar proportions (between 
37% and 55%) of global posts within organisations, whereas the discriminated
status induces only global posts. 

\hfill\break
###### Distribution of global post proportions over whether an organisation has government power or not.

```{r}
plt_prop_glob_gov_pow <- ggplot(na.omit(joined_data[, c("prop_global", "gov_pow")]),aes(x = as.factor(gov_pow), y = prop_global)) +
  geom_boxplot() +
  labs(title = "Global proportion of all posts by Government Power",
       x = "Government Power",
       y = "Proportion of global posts") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
#ggsave("Prop_glob_gov_pow.jpg", plot = plt_prop_glob_gov_pow, bg="white")
plt_prop_glob_gov_pow
```

Interpretation: Organisations, which have government power tend to slightly have
lower proportions of global posts (around 35%) compared to the organisations 
which do not have government power, where roughly half of the posts are global.

\hfill\break
###### Distribution of global post proportions over whether an organisation has regional autonomy or not.

```{r}
plt_prop_glob_reg_auton <- ggplot(na.omit(joined_data[, c("prop_global", "reg_autonom")]),aes(x = as.factor(reg_autonom), y = prop_global)) +
  geom_boxplot() +
  labs(title = "Global proportion of all posts by Regional Autonomy",
       x = "Regional Autonomy",
       y = "Proportion of global posts") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
#ggsave("Prop_glob_reg_autonom.jpg", plot = plt_prop_glob_reg_auton, bg="white")
plt_prop_glob_reg_auton
```

Interpretation: Organisations, which have regional autonomy tend to slightly have
lower proportions of global posts (around 30%) compared to the organisations 
which do not have regional autonomy, where roughly 40% of posts are global.

\hfill\break
###### Distribution of global post proportions over whether an organisation experiences separatism or irridentism or not.

```{r}
plt_prop_glob_sep_irred <- ggplot(na.omit(joined_data[, c("prop_global", "sep_irred")]),aes(x = as.factor(sep_irred), y = prop_global)) +
  geom_boxplot() +
  labs(title = "Global proportion of all posts by Separatism / Irridentism",
       x = "Separatism / Irridentism",
       y = "Proportion of global posts") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
#ggsave("Prop_glob_sep_irred.jpg", plot = plt_prop_glob_sep_irred, bg="white")
plt_prop_glob_sep_irred
```

Interpretation: Organisations, which experience separatism or irridentism tend 
to slightly have lower proportions of global posts (around 30%) compared to  
organisations do not experience irridentism or separatism, where roughly 40% of 
posts are global.

\hfill\break
###### Distribution of global post proportions over whether an organisation use an ethnic claim or not.

```{r}
plt_prop_glob_eth_claim <- ggplot(na.omit(joined_data[, c("prop_global", "eth_claim")]),aes(x = as.factor(eth_claim), y = prop_global)) +
  geom_boxplot() +
  labs(title = "Global proportion of all posts by Ethnic Claim",
       x = "Ethnic Claim",
       y = "Proportion of global posts") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
#ggsave("Prop_glob_eth_claim.jpg", plot = plt_prop_glob_eth_claim, bg="white")
plt_prop_glob_eth_claim
```

Interpretation: Whether an organisation uses an ethnic claim or not seems to not
have a too decisive role on whether posts are global are not, with similar global
post proportions of around 37%.

\hfill\break
###### Distribution of global posts based on whether an organisation's group has a war history (Count variable indicating number of conflict onsets this group has previously experienced).

```{r, warning=FALSE, message=FALSE}
plt_glob_prop_war_hist <- ggplot(joined_data, aes(x = warhist, y = prop_global)) +
  geom_jitter() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Proportion of Global Posts by War History",
       x = "War History",
       y = "Proportion of global posts") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(vjust = -1),
    axis.title.y = element_text(vjust = 2)
  ) 
#ggsave("Glob_Prop_war_hist.jpg", plot = plt_glob_prop_war_hist, bg="white")
plt_glob_prop_war_hist
```

Interpretation: So far, all organisations have not experienced more than four 
conflict onsets. Organisations which have not experienced conflict onsets have
slightly higher proportions of global posts, compared to the organisations which
have experienced two or more conflict onsets. However, the proportions are not 
unambiguous, since the proportions of global posts of organisations which have 
not experienced conflict onsets vary strongly between 0 and 100% global posts.

\hfill\break
\hfill\break

### Regressions
\hfill\break
#### Global Max Models: 
\hfill\break
DV: global_max & country_max & global with Fixed effects & Clustered Errors
\hfill\break

##### Multiethnic Flag and Global Max:     
\hfill\break
This analysis deals with the question whether multiethnic organisations are 
more inclined to have a conversation about global topics.

```{r, results="asis", warning=FALSE}
model_global_max_multethn_flag <- felm(global_max ~ multiethnic_flag| gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_global_max_multethn_flag, type="latex", title="Regression Results for Global Max by Multiethnic Flag", style="default", single.row=TRUE, digits=3)
```  

Interpretation: Messages from multiethnic organizations are significantly more likely to discuss global topics.

\hfill\break
#### Country Max Models

##### Electoral Participation and Country Max:    
\hfill\break
This analysis is about if electoral participation of an organisation leads to 
more discussions on a national level.

```{r, results="asis", warning=FALSE}
model_cntry_max_elect_part <- felm(country_max ~ elect_part | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_cntry_max_elect_part, type="latex", title="Regression Results for Country Max by Electoral Participation", style="default", single.row=TRUE, digits=3)
```  

Interpretation: The effect of electoral participation is not significant.

##### Static exclusion status and Country Max:    
\hfill\break
Here we try to find the impact of an exclusionary status of an organsiation on 
the nationalness of organisations' posts.  

```{r, results="asis", warning=FALSE}
model_cntry_max_status_excl_epr_static <- felm(country_max ~ status_excl_epr_static | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_cntry_max_status_excl_epr_static, type="latex", title="Regression Results for Country Max by Exclusionary Status", style="default", single.row=TRUE, digits=3)
```  

Interpretation: Not significant; Maybe could do a model with the exclusion status 
per year as well (data needs to be grouped beforehand)

\hfill\break
#### Global Models


##### Country and Global:   
\hfill\break
Here, we check whether posts within a country are more focussed on national or 
global topics.
```{r, eval=FALSE, include=FALSE}
#Disclaimer: Only with year fixed effects; otherwise potential collinearity issues. 
```
\hfill\break
```{r, results="asis", warning=FALSE}
model_global_gwidx <- felm(global ~ as.factor(gwid.x) | year| 0 | year, data = joined_data)
stargazer(model_global_gwidx, type="latex", title="Regression Results for Global Posts by Country", style="default", single.row=TRUE, digits=3)
```  

Interpretation: Some countries show a significant effect on whether the conversation is global or national, 
albeit it is only a moderate effect.

\hfill\break
##### Organisation age and Global:   
\hfill\break
This statistical model checks whether topics in posts of organisations become 
rather national or global with rising age of the organisations.  

```{r, results="asis", warning=FALSE}
model_global_org_age <- felm(global ~ org_age | gwid.x + year | 0 |  gwid.x +year, data = joined_data)
stargazer(model_global_org_age, type="latex", title="Regression Results for Global Posts by Organisation Age", style="default", single.row=TRUE, digits=3)
```  

Interpretation: The age of an organisation has a slightly significant and moderately negative effect on the 
choice of global issues in the discourse.

\hfill\break
##### Static exclusion status and Global:  
\hfill\break
This model investigates whether the exclusion status of an organisation influences
whether the conversation is global or national.

```{r, results="asis", warning=FALSE}
model_global_status_excl_epr_static <- felm(global ~ status_excl_epr_static | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_global_status_excl_epr_static, type="latex", title="Regression Results for Global Posts by Exclusion Status", style="default", single.row=TRUE, digits=3)
```

Interpretation: The model is not significant.

\hfill\break
##### Education language and Global:  
\hfill\break
This analysis examines whether the language in education influences whether the 
posts of organisations are global or national.

```{r, results="asis", warning=FALSE}
model_global_ed_language1 <- felm(global ~ ed_language1 | gwid.x +year | 0 | gwid.x +year, data = joined_data)
stargazer(model_global_ed_language1, type="latex", title="Regression Results for Global Posts by Education Language", style="default", single.row=TRUE, digits=3)
```

Interpretation: The language in education has a significant impact on whether the conversation is rather global 
or national.  
Disclaimer: Collinearity issues detected

\hfill\break
\hfill\break
#### Proportion of global posts

##### Primary platform and proportion of global posts
\hfill\break
Doesn't work atm, as the current subsample only contains one category (only
one platform, thus, no variability given)

```{r,  results="asis", warning=FALSE}
model_glob_prop_primary <- felm(prop_global ~ primary | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_prob_primary, type="latex", title="Regression Results for Proportion of Global Posts by Primary Platform", style="default", single.row=TRUE, digits=3)
```  
\hfill\break
##### Electoral participation and proportion of global posts
\hfill\break
```{r,  results="asis", warning=FALSE}
model_glob_prop_elect_part <- felm(prop_global ~ elect_part | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_prop_elect_part, type="latex", title="Regression Results for Proportion of Global Posts by Electoral Participation", style="default", single.row=TRUE, digits=3)
``` 

Interpretation: Electoral participation has a negative but statistically 
insignificant effect on the proportion of global posts, while the model 
explains 65.3% of the variance in the dependent variable.

\hfill\break
##### Channel Type and proportion of global posts
\hfill\break
Doesn't work atm, as the current subsample only contains one category (only
one platform, thus, no variability given)

```{r,  results="asis", warning=FALSE}
model_glob_prop_channel_type <- felm(prop_global ~ channel_type | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_prop_channel_type, type="latex", title="Regression Results for Proportion of Global Posts by Channel Type", style="default", single.row=TRUE, digits=3)
``` 

\hfill\break
##### Video/Image (Media) binary flag and proportion of global posts
\hfill\break
```{r,  results="asis", warning=FALSE}
model_glob_prop_media_flag <- felm(prop_global ~ video_or_image_flag | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_prop_media_flag, type="latex", title="Regression Results for Proportion of Global Posts by Media flag (video/image)", style="default", single.row=TRUE, digits=3)
``` 

Interpretation: The presence of video or image content has a negative but 
statistically insignificant effect on the proportion of global posts, while the 
model explains 63.3% of the variance in the dependent variable.

\hfill\break
##### Language prediction and proportion of global posts
\hfill\break
```{r,  results="asis", warning=FALSE}
model_glob_prop_lang_pred <- felm(prop_global ~ as.factor(language_pred) | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_prop_lang_pred, type="latex", title="Regression Results for Proportion of Global Posts by Language Prediction", style="default", single.row=TRUE, digits=3)
``` 

Interpretation: The predicted language of a post has a significant effect on the 
proportion of global posts, with most languages showing a positive association, 
while a few, such as Bosnian and Piedmontese, have a negative effect; the model 
explains 65.7% of the variance in the dependent variable.

\hfill\break
##### Education Language and proportion of global posts
\hfill\break
```{r,  results="asis", warning=FALSE}
model_glob_prop_educ_lang <- felm(prop_global ~ as.factor(ed_language1) | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_prop_educ_lang, type="latex", title="Regression Results for Proportion of Global Posts by Education Language", style="default", single.row=TRUE, digits=3)
``` 

Interpretation: The primary education language has a significant effect on the 
proportion of global posts, with Bosnian, Hungarian, Romano-Serbian, and Slovak 
increasing the proportion, while English, French, Welsh, Basque, Galician, 
Eastern Punjabi, Serbian, and especially Flemish decrease it; the model explains 
66.8% of the variance in the dependent variable.

\hfill\break
##### Statusname and proportion of global posts
\hfill\break
```{r,  results="asis", warning=FALSE}
model_glob_prop_statusname <- felm(prop_global ~ as.factor(statusname) | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_prop_statusname, type="latex", title="Regression Results for Proportion of Global Posts by Statusname", style="default", single.row=TRUE, digits=3)
``` 

Interpretation: The status category of a group has a significant negative effect 
on the proportion of global posts, with senior partners showing the strongest 
negative effect, followed by monopoly, powerless, dominant, and junior partner 
groups, while the model explains 80.9% of the variance in the dependent variable.

\hfill\break
##### Government power and proportion of global posts
\hfill\break
```{r,  results="asis", warning=FALSE}
model_glob_prop_gov_pow <- felm(prop_global ~ gov_pow | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_prop_gov_pow, type="latex", title="Regression Results for Proportion of Global Posts by Government Power", style="default", single.row=TRUE, digits=3)
``` 

Interpretation: Government power has a significant negative effect on the 
proportion of global posts, indicating that as government power increases, the 
likelihood of discussing global topics decreases, while the model explains 61.6% 
of the variance in the dependent variable.

\hfill\break
##### Region and proportion of global posts
\hfill\break
Doesn't work; probably data too imbalanced.

```{r,  results="asis", warning=FALSE}
model_glob_prop_region <- felm(prop_global ~ as.factor(region) | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_prop_region, type="latex", title="Regression Results for Proportion of Global Posts by Region", style="default", single.row=TRUE, digits=3)
``` 

\hfill\break
##### Ethnic claim and proportion of global posts
\hfill\break
```{r,  results="asis", warning=FALSE}
model_glob_prop_eth_claim <- felm(prop_global ~ eth_claim | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_prop_eth_claim, type="latex", title="Regression Results for Proportion of Global Posts by Ethnic Claim", style="default", single.row=TRUE, digits=3)
``` 

Interpretation: Ethnic claims have a significant positive effect on the 
proportion of global posts, suggesting that higher levels of ethnic claims are 
associated with an increased likelihood of discussing global topics, while the 
model explains 61.5% of the variance in the dependent variable.

\hfill\break
##### Separatism / Irridentism and proportion of global posts
\hfill\break
```{r,  results="asis", warning=FALSE}
model_glob_prop_sep_irred <- felm(prop_global ~ sep_irred | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_prop_sep_irred, type="latex", title="Regression Results for Proportion of Global Posts by Separatism/Irridentism", style="default", single.row=TRUE, digits=3)
```

Interpretation: Separatism and irredentism have a significant negative effect on 
the proportion of global posts, indicating that groups advocating for separatist 
or irredentist claims are slightly less likely to engage with global topics, 
while the model explains 62.8% of the variance in the dependent variable.

\hfill\break
##### Regional autonomy and proportion of global posts
\hfill\break
```{r,  results="asis", warning=FALSE}
model_glob_prop_reg_autonom <- felm(prop_global ~ reg_autonom | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_prop_reg_autonom, type="latex", title="Regression Results for Proportion of Global Posts by Regional Autonomy", style="default", single.row=TRUE, digits=3)
```

Interpretation: Regional autonomy has a significant negative effect on the 
proportion of global posts, suggesting that groups with greater regional 
autonomy are slightly less likely to engage with global topics, while the model 
explains 62.0% of the variance in the dependent variable.

\hfill\break
\hfill\break

### New datasets: Global Max
\hfill\break
#### Primary and global max
\hfill\break
Doesn't work atm, as the current subsample only contains one category (only
primary channels, thus, no variability given)

```{r,  results="asis", warning=FALSE}
model_glob_max_primary <- felm(global_max ~ primary | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_max_primary, type="latex", title="Regression Results for  maximal global topic probability by Primary Account", style="default", single.row=TRUE, digits=3)
```

\hfill\break
#### Electoral Participation and global max
\hfill\break
```{r,  results="asis", warning=FALSE}
model_glob_max_elect_part <- felm(global_max ~ elect_part | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_max_elect_part, type="latex", title="Regression Results for maximal global topic probability by Electoral Participation", style="default", single.row=TRUE, digits=3)
```

Interpretation: Electoral participation has a significant negative effect on the 
maximal global topic probability, indicating that higher electoral participation 
is associated with a lower likelihood of global issue engagement, while the 
model explains  only5.6% of the variance in the dependent variable.

\hfill\break
#### Channel Type and global max
\hfill\break
Doesn't work atm, as the current subsample only contains one category (only
one platform, thus, no variability given)

```{r,  results="asis", warning=FALSE}
model_glob_max_chan_type <- felm(global_max ~ channel_type | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_max_chan_type, type="latex", title="Regression Results for maximal global topic probability by Channel Type", style="default", single.row=TRUE, digits=3)
```

\hfill\break
#### Organisation and global max (Organisation level)
\hfill\break
```{r,  results="asis", warning=FALSE}
model_glob_max_org <- felm(global_max ~ as.factor(org_id_from_coll) | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_max_org, type="latex", title="Regression Results for maximal global topic probability by Organisation", style="default", single.row=TRUE, digits=3)
```

Interpretation: The organisation a post originates from has a significant effect 
on the maximal global topic probability, with some organisations showing positive 
associations and others negative, while the model explains 11.6% of the variance 
in the dependent variable.

\hfill\break
#### Video/Image and global max 
\hfill\break
```{r,  results="asis", warning=FALSE}
model_glob_max_media_flag <- felm(global_max ~ video_or_image_flag | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_max_media_flag, type="latex", title="Regression Results for maximal global topic probability by Media Flag", style="default", single.row=TRUE, digits=3)
```

Interpretation: The presence of video or image content has a small and 
statistically insignificant effect on the maximal global topic probability, 
while the model explains only 5.3% of the variance in the dependent variable.

\hfill\break
#### Language Prediction and global max
\hfill\break
```{r,  results="asis", warning=FALSE}
model_glob_max_lang_pred <- felm(global_max ~ as.factor(language_pred) | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_max_lang_pred, type="latex", title="Regression Results for maximal global topic probability by Language", style="default", single.row=TRUE, digits=3)
```

Interpretation: The predicted language of a post has a significant effect on the 
maximal global topic probability, with most languages showing a positive 
association, while Bosnian (bs), Piedmontese (pms), and Uzbek (uz) exhibit 
negative effects. However, the effects for Arabic (ar), Greek (el), Latin (la), 
Dutch (nl), Swedish (sv), Tagalog (tl), Vietnamese (vi), and Chinese (zh) are 
statistically insignificant. The model explains 5.9% of the variance in the 
dependent variable.

\hfill\break
#### Education Language and global max
\hfill\break
```{r,  results="asis", warning=FALSE}
model_glob_max_educ_lang <- felm(global_max ~ as.factor(ed_language1) | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_max_educ_lang, type="latex", title="Regression Results for maximal global topic probability by Education Language", style="default", single.row=TRUE, digits=3)
```

Interpretation: The primary education language has a significant effect on the 
maximal global topic probability, with Bosnian (bos), Catalan (cat), Hungarian 
(hun), and Romano-Serbian (rsb) showing positive effects, while Welsh (cym), 
English (eng), French (fra), Galician (glg), Serbian (srp), and especially West 
Flemish (vls) show negative effects. The effects for Basque (eus), Slovak (slk), 
and Punjabi (pan) are statistically insignificant. For some languages (Nivaclé 
(cag), German (due), Polish (pol), Portuguese (por), Quecha (que), Cusco Quecha 
(quz), Spanish (spa)) no coefficient could be calculated. The model explains 
6.2% of the variance in the dependent variable.

\hfill\break
#### Statusname and global max
\hfill\break
```{r,  results="asis", warning=FALSE}
model_glob_max_status <- felm(global_max ~ as.factor(statusname) | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_max_status, type="latex", title="Regression Results for maximal global topic probability by Statusname", style="default", single.row=TRUE, digits=3)
```

Interpretation: The status category of a group has a significant negative effect 
on the maximal global topic probability, with senior partners showing the 
strongest negative effect, followed by monopoly, dominant, junior partner, and 
powerless groups, while the model explains 6.6% of the variance in the dependent 
variable.

\hfill\break
#### Government Power and global max 
\hfill\break
```{r,  results="asis", warning=FALSE}
model_glob_max_gov_pow <- felm(global_max ~ gov_pow | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_max_gov_pow, type="latex", title="Regression Results for maximal global topic probability by Government Power", style="default", single.row=TRUE, digits=3)
```

Interpretation: Government power has a significant negative effect on the 
maximal global topic probability, indicating that as government power increases, 
the likelihood of engaging with global topics decreases, while the model 
explains 6.2% of the variance in the dependent variable.


\hfill\break
#### Region and global max

```{r,  results="asis", warning=FALSE}
model_glob_max_region <- felm(global_max ~ as.factor(region) | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_max_region, type="latex", title="Regression Results for maximal global topic probability by Region", style="default", single.row=TRUE, digits=3)
```

Interpretation: The regression model for maximal global topic probability by 
region could not be estimated due to an error, likely caused by insufficient 
variation, missing data, or singular matrix issues in the region variable.

\hfill\break
#### Ethnic claim and global max 
\hfill\break
```{r,  results="asis", warning=FALSE}
model_glob_max_eth_claim <- felm(global_max ~ eth_claim | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_max_eth_claim, type="latex", title="Regression Results for maximal global topic probability by Ethnic Claim", style="default", single.row=TRUE, digits=3)
```

Interpretation: Ethnic claims have a significant positive effect on the maximal 
global topic probability, indicating that higher levels of ethnic claims are 
associated with a greater likelihood of engaging with global topics, while the 
model explains 6.1% of the variance in the dependent variable.

\hfill\break
#### Separatism/Irridentism and global max 

```{r,  results="asis", warning=FALSE}
model_glob_max_sep_irred <- felm(global_max ~ sep_irred | gwid.x + year | 0 | gwid.x + year, data = joined_data, na.action = na.omit)
stargazer(model_glob_max_sep_irred, type="latex", title="Regression Results for maximal global topic probability by Separatism/Irridentism", style="default", single.row=TRUE, digits=3)
```

Interpretation: The regression model for maximal global topic probability by 
separatism/irredentism could not be estimated due to a matrix computation error, 
likely caused by missing data, collinearity, or singularity issues in the 
variable.

\hfill\break
#### Regional Autonomy and global max 
\hfill\break
```{r,  results="asis", warning=FALSE}
model_glob_max_reg_autonom <- felm(global_max ~ reg_autonom | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_max_reg_autonom, type="latex", title="Regression Results for maximal global topic probability by Regional Autonomy", style="default", single.row=TRUE, digits=3)
```

Interpretation: Regional autonomy has a small but significant positive effect on 
the maximal global topic probability, suggesting that higher levels of regional 
autonomy are associated with a slightly greater likelihood of engaging with 
global topics, while the model explains 6.0% of the variance in the dependent 
variable.

\hfill\break
\hfill\break
### New datasets: Country Max

#### Primary and country max

```{r,  results="asis", warning=FALSE}
model_cntry_max_primary <- felm(country_max ~ primary | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_cntry_max_primary, type="latex", title="Regression Results for  maximal country topic probability by Primary Account)", style="default", single.row=TRUE, digits=3)
```

Interpretation: The regression model for maximal country topic probability by 
primary account could not be estimated due to an error, likely caused by the 
primary variable having only one level or missing values, preventing the 
application of contrasts in the model.

\hfill\break
#### Electoral Participation and country max
\hfill\break
```{r,  results="asis", warning=FALSE}
model_cntry_max_elect_part <- felm(country_max ~ elect_part | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_cntry_max_elect_part, type="latex", title="Regression Results for maximal country topic probability by Electoral Participation", style="default", single.row=TRUE, digits=3)
```

Interpretation: Electoral participation has a small and statistically 
insignificant effect on the maximal country topic probability, while the model 
explains 5.1% of the variance in the dependent variable.


\hfill\break
#### Channel Type and country max

```{r,  results="asis", warning=FALSE}
model_cntry_max_chan_type <- felm(country_max ~ channel_type | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_cntry_max_chan_type, type="latex", title="Regression Results for maximal country topic probability by Channel Type", style="default", single.row=TRUE, digits=3)
```

Interpretation: The regression model for maximal country topic probability by 
channel type could not be estimated due to an error, likely caused by the 
channel_type variable having only one level or missing values, preventing the 
application of contrasts in the model.

\hfill\break
#### Organisation and country max (Organisation level)
\hfill\break
```{r,  results="asis", warning=FALSE}
model_cntry_max_org <- felm(country_max ~ as.factor(org_id_from_coll) | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_cntry_max_org, type="latex", title="Regression Results for maximal country topic probability by Organisation", style="default", single.row=TRUE, digits=3)
```

Interpretation: The organisation a post originates from has a significant effect 
on the maximal country topic probability, with some organisations showing 
positive associations and others negative, while the model explains 10.3% of the 
variance in the dependent variable.

\hfill\break
#### Video/Image and country max 
\hfill\break
```{r,  results="asis", warning=FALSE}
model_cntry_max_media_flag <- felm(country_max ~ video_or_image_flag | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_cntry_max_media_flag, type="latex", title="Regression Results for maximal country topic probability by Media Flag", style="default", single.row=TRUE, digits=3)
```

Interpretation: The presence of video or image content has a small but 
significant positive effect on the maximal country topic probability, while the 
model explains 5.1% of the variance in the dependent variable.

\hfill\break
#### Language Prediction and country max
\hfill\break
```{r,  results="asis", warning=FALSE}
model_cntry_max_lang_pred <- felm(country_max ~ as.factor(language_pred) | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_cntry_max_lang_pred, type="latex", title="Regression Results for maximal country topic probability by Language", style="default", single.row=TRUE, digits=3)
```

Interpretation: The predicted language of a post has a significant effect on the 
maximal country topic probability, with Interlingue (ie), Uzbek (uz) and 
Ukrainian (uk) having significant negative effects. The effects for Arabic (ar), 
Bosnian (bs), Cebuano (ceb), German (de), Greek (el), Icelandic (is), Latin 
(la), Malagasy (mg), Macedonian (mk), Malay (ms), Occitan (oc), Russian (ru), 
Slovenian (sl), Swedish (sv), Thai (th), Tagalog (tl), Vietnamese (vi), and 
Chinese (zh) are statistically insignificant, while the remaining languages show 
positive associations. The model explains 5.9% of the variance in the dependent 
variable.

\hfill\break
#### Education Language and country max
\hfill\break
```{r,  results="asis", warning=FALSE}
model_cntry_max_ed_lang <- felm(country_max ~ as.factor(ed_language1) | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_cntry_max_ed_lang, type="latex", title="Regression Results for maximal country topic probability by Education Language", style="default", single.row=TRUE, digits=3)
```

Interpretation: The primary education language has a significant effect on the 
maximal country topic probability, with Serbian having a significant negative 
effect. The effects for Bosnian, Galician, Hungarian, Serbo-Croatian, and Slovak 
are statistically insignificant, while the remaining languages show positive 
associations. No coefficient could be calculated for Tosk Albanian, Nivaclé, 
German, Polish, Portuguese, Quechua, Cusco Quechua, and Spanish. The model 
explains 6.2 percent of the variance in the dependent variable.

\hfill\break
#### Statusname and country max
\hfill\break
```{r,  results="asis", warning=FALSE}
model_cntry_max_status <- felm(country_max ~ as.factor(statusname) | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_cntry_max_status, type="latex", title="Regression Results for maximal country topic probability by Statusname", style="default", single.row=TRUE, digits=3)
```

Interpretation: The status category of a group has a significant positive effect 
on the maximal country topic probability, with senior partners showing the 
strongest positive effect, followed by monopoly, powerless, junior partner, and 
dominant groups. The model explains 7.3 percent of the variance in the dependent 
variable.

\hfill\break
#### Government power and country max 
\hfill\break
```{r,  results="asis", warning=FALSE}
model_cntry_max_gov_pow <- felm(country_max ~ gov_pow | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_cntry_max_gov_pow, type="latex", title="Regression Results for maximal country topic probability by Government Power", style="default", single.row=TRUE, digits=3)
```

Interpretation: Government power has no significant effect on the maximal 
country topic probability, while the model explains 4.6 percent of the variance 
in the dependent variable.

\hfill\break
#### Region and country max

```{r,  results="asis", warning=FALSE}
model_country_max_region <- felm(country_max ~ as.factor(region) | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_country_max_region, type="latex", title="Regression Results for maximal country topic probability by Region", style="default", single.row=TRUE, digits=3)
```

Interpretation: The regression model for maximal country topic probability by 
region could not be estimated due to an error, likely caused by insufficient 
variation, missing data, or singular matrix issues in the region variable.

\hfill\break
#### Ethnic claim and country max 
\hfill\break
```{r,  results="asis", warning=FALSE}
model_cntry_max_eth_claim <- felm(country_max ~ eth_claim | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_cntry_max_eth_claim, type="latex", title="Regression Results for maximal country topic probability by Ethnic claim", style="default", single.row=TRUE, digits=3)
```

Interpretation: Ethnic claims have a significant negative effect on the maximal 
country topic probability, while the model explains 4.6 percent of the variance 
in the dependent variable.

\hfill\break
#### Separatism/Irridentism and country max 
\hfill\break
```{r,  results="asis", warning=FALSE}
model_cntry_max_sep_irred <- felm(country_max ~ sep_irred | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_cntry_max_sep_irred, type="latex", title="Regression Results for maximal country topic probability by Separatism/Irridentism", style="default", single.row=TRUE, digits=3)
```

Interpretation: Separatism and irredentism have a small but significant positive 
effect on the maximal country topic probability, while the model explains 4.8 
percent of the variance in the dependent variable.

\hfill\break
#### Regional Autonomy and country max 
\hfill\break
```{r,  results="asis", warning=FALSE}
model_cntry_max_reg_autonom <- felm(country_max ~ reg_autonom | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_cntry_max_reg_autonom, type="latex", title="Regression Results for maximal country topic probability by Regional Autonomy", style="default", single.row=TRUE, digits=3)
```

Interpretation: Regional autonomy has a small but significant positive effect on 
the maximal country topic probability, with the model explaining 4.8 percent of 
the variance in the dependent variable.

\hfill\break
\hfill\break
### New datasets: Global
\hfill\break
#### Primary and global

```{r,  results="asis", warning=FALSE}
model_global_primary <- felm(global ~ primary | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_global_primary, type="latex", title="Regression Results for  Global Posts by Primary Account)", style="default", single.row=TRUE, digits=3)
```

Interpretation: The model could not be estimated because the variable "primary" 
does not have at least two levels so far.

\hfill\break
#### Electoral Participation and global 
\hfill\break
```{r,  results="asis", warning=FALSE}
model_global_elect_part <- felm(global ~ elect_part | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_global_elect_part, type="latex", title="Regression Results for Global Posts by Electoral Participation", style="default", single.row=TRUE, digits=3)
```

Interpretation: Electoral participation has a negative but statistically 
insignificant effect on the probability of a post being classified as global.


\hfill\break
#### Channel Type and global 

```{r,  results="asis", warning=FALSE}
model_global_chan_type <- felm(global ~ channel_type | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_global_chan_type, type="latex", title="Regression Results for Global Posts by Channel Type", style="default", single.row=TRUE, digits=3)
```

Interpretation: The model could not be estimated because the variable channel 
type does not have at least two levels so far.

\hfill\break
#### Organisation and global (Organisation level)
\hfill\break
```{r,  results="asis", warning=FALSE}
model_glob_org <- felm(global ~ as.factor(org_id_from_coll) | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_org, type="latex", title="Regression Results for Global Posts by Organisation", style="default", single.row=TRUE, digits=3)
```

Interpretation: The results indicate that several organisations show a negative 
and significant relationship with global posts. This suggests that these 
organisations are less likely to post globally relevant content. Most other 
organisations either show a positive effect or are insignificant, meaning there 
is no clear relationship between their activity and global post probability.

\hfill\break
#### Video/Image Flag and global 
\hfill\break
```{r,  results="asis", warning=FALSE}
model_glob_media_flag <- felm(global ~ video_or_image_flag | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_media_flag, type="latex", title="Regression Results for Global Posts by Media Flag", style="default", single.row=TRUE, digits=3)
model_glob_media_flag
```

Interpretation: The results show that the presence of video or image content has
a negative but insignificant effect on global posts. 

\hfill\break
#### Language Prediction and global 
\hfill\break
```{r,  results="asis", warning=FALSE}
model_glob_lang_pred <- felm(global ~ language_pred | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_lang_pred, type="latex", title="Regression Results for Global Posts by Language", style="default", single.row=TRUE, digits=3)
```

Interpretation: Most languages have a significant positive effect on the 
likelihood of a post being classified as global, with particularly high 
coefficients for Irish (1.169), Icelandic (1.150), and Occitan (0.856), while 
Piedmontese (-0.131) is the only language with a significant negative effect. 
Japanese (ja), Latin (la) and Malay (ms) are insignificant.

\hfill\break
#### Education Language and global 
\hfill\break
```{r,  results="asis", warning=FALSE}
model_glob_ed_lang <- felm(global ~ as.factor(ed_language1) | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_ed_lang, type="latex", title="Regression Results for Global Posts by Education Language", style="default", single.row=TRUE, digits=3)
```

Interpretation: Most education languages have a significant effect on the 
likelihood of a post being classified as global, with Bosnian (0.260), Hungarian 
(0.251), Romano-Serbian (rsb, 0.286), and Slovak (0.234) showing significant 
positive effects, while Welsh (-0.599), English (-0.550), Basque (-0.112), 
French (-0.527), Galician (-0.085), Eastern Punjabi (-0.382), Serbian (srp, 
-0.054), and Flemish (-0.753) exhibit significant negative effects; Catalan 
(-0.030) is insignificant, and no coefficients were calculated for Alsatian, 
Nivaclé, German, Polish, Portuguese, Quechuan languages and Spanish .

\hfill\break
#### Status and global 
\hfill\break
```{r,  results="asis", warning=FALSE}
model_glob_status <- felm(global ~ as.factor(statusname) | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_status, type="latex", title="Regression Results for Global Posts by Statusname", style="default", single.row=TRUE, digits=3)
```

Interpretation: All status categories have a significant negative effect on the 
likelihood of a post being classified as global, with Senior Partner (-1.492) 
and Monopoly (-1.020) showing the strongest negative associations, followed by 
Powerless (-0.787), Dominant (-0.743), and Junior Partner (-0.723).

\hfill\break
#### Government power and global 
\hfill\break
```{r,  results="asis", warning=FALSE}
model_glob_gov_pow <- felm(global ~ gov_pow | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_gov_pow, type="latex", title="Regression Results for Global Posts by Government Power", style="default", single.row=TRUE, digits=3)
```

Interpretation: Government power has a significant negative effect on the 
likelihood of a post being classified as global, with a coefficient of -0.068.


\hfill\break
#### Region and global

```{r,  results="asis", warning=FALSE}
model_glob_region <- felm(global ~ as.factor(region) | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_region, type="latex", title="Regression Results for Global Posts by Region", style="default", single.row=TRUE, digits=3)
```

Interpretation: The model for global posts by region could not be estimated due 
to a dimensionality issue, likely caused by collinearity or a lack of variation 
in the region variable.

\hfill\break
#### Ethnic claim and global 
\hfill\break
```{r,  results="asis", warning=FALSE}
model_glob_eth_claim <- felm(global ~ eth_claim | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_eth_claim, type="latex", title="Regression Results for Global Posts by Ethnic Claim", style="default", single.row=TRUE, digits=3)
```

Interpretation: Ethnic claim has a significant and strong positive effect 
(0.554) on the likelihood of global posts, indicating that groups making ethnic 
claims are more likely to produce globally classified posts.

\hfill\break
#### Separatism/Irridentism and global 
\hfill\break
```{r,  results="asis", warning=FALSE}
model_glob_sep_irred <- felm(global ~ sep_irred | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_sep_irred, type="latex", title="Regression Results for Global Posts by Separatism/Irridentism", style="default", single.row=TRUE, digits=3)
```

Interpretation: Separatism/Irridentism has a significant negative effect 
(-0.058) on the likelihood of global posts, suggesting that groups advocating 
for separatist or irredentist claims are less likely to produce globally 
classified posts.

\hfill\break
#### Regional Autonomy and global 
\hfill\break
```{r,  results="asis", warning=FALSE}
model_glob_reg_autonom <- felm(global ~ reg_autonom | gwid.x + year | 0 | gwid.x + year, data = joined_data)
stargazer(model_glob_reg_autonom, type="latex", title="Regression Results for Global Posts by Regional Autonomy", style="default", single.row=TRUE, digits=3)
```

Interpretation: Regional autonomy has a significant negative effect (-0.063) on 
the likelihood of global posts, indicating that groups with greater regional 
autonomy are less likely to produce globally classified content.